---
title: "DO ART NCD Supplement"
author: ""
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  word_document:
    reference_docx: word_styles.docx

---

```{r setup, include = F, echo = F, warning = F, message = F}

rm(list=ls())

# Load packages

library(dplyr)
library(tidyr)
library(data.table)
library(ggplot2)

# Table formatting packages
library(janitor)
library(tables)
library(flextable)

# Regression packages
library(geepack)

# Load data

dir <- "C:/Users/msahu/Documents/Other_Research/DO_ART_NCD/"
in_dir <- paste0(dir, "0_data/3_cleaned_data/")

# DO WE WANT TO COMBINE COMMUNITY AND HYBRID HERE??

ncd_merged_subset <- readRDS(paste0(in_dir, "ncd_merged_subset.rds")) %>% 
  mutate(armR = case_when(arm == "Clinic arm" ~ "Clinic follow-up",
                          arm == "Community arm" ~ "Community follow-up",
                          arm == "Hybrid arm" ~ "Community follow-up" ))



ncd_noHybrid <- ncd_merged_subset %>% filter(arm!= "Hybrid arm")
round_digits = 2
p_digits = 3

```


# Appendix tables 

+ Appendix Section 1 Codebook (included with main paper)
+ Appendix Section 2, Table 1: Change in cardiovascular risk from baseline to endline, by trial arm and gender (AHRI site only, N = 350)
+ Appendix Section 2, Table 2: Descriptive statistics of cardiovascular risk in the DO ART study, by site and including Uganda (N = 1315) 

### Page Break


## Appendix Table 1: Change in cardiovascular risk from baseline to endline, by trial arm and gender (AHRI site only, N = 350)

&nbsp;


```{r, echo = F, warning = F, message = F, ft.split = T, ft.keepnext = F, results = 'asis'}


# Set up -------------------------------------------------------------

headings <- data.frame(
  section = c("A", "B", "C"),
  title = c( "", 
             "ii) Lifestyle and other risk",
              "iii) Cardiovascular Risk")
)

# A) Demographics
A_vars = c(
  "age_cat",
  "genderR"
  )
A_var_labels = c(
  "Age",
  "Gender"
  )

# B) Lifestyle and Other Risk

B_vars = c(  
  "smoking_cat",
  "exer_cat",
  "veg_cat",
  "stroke_cat")
B_var_labels = c(
  "Smoking Status  \n [Baseline]",
  "Days of exercise (per week) \n [Endline]",
  "Vegetable intake \n [Endline]",
   "Prior stroke or heart attack  \n [Endline]")


# C) Cardiovascular risk
C_vars = c(
  "bp_cat_exit", 
  "bmi_cat_exit", 
  "a1c_cat_exit", 
  "total_cholesterol_exit",
  "who_cvd_risk_exit")
C_var_labels = c(
  "Blood pressure \n [Endline]",
   "BMI (kg/m^2) \n [Endline]",
   "Hemoglobin A1C (%) \n [Endline]",
   "Total cholesterol (mg/dL) \n [Endline]",
   "10-year CVD risk score \n [Endline]")

# D) Change in CVD risk
D_vars = c(  
  "bmi_diff",
  "sbp_diff")
D_var_labels = c(
  "Change in BMI, baseline to endline  \n [AHRI only]",
  "Change in Systolic Blood pressure, baseline to endline  \n [AHRI only]" )


table_vars <- data.frame(
  
  var_name = c(D_vars),

  var_label = c(D_var_labels)) %>% 
  
  mutate( 
    
    section = case_when(
      var_name %in% c(D_vars) ~ "D"))
  
  
# Descriptive Proportion Table ----------------------------------------------------

col_headings_mean <- c(
  "Change in CVD risk",
  "Clinic Arm \n Mean (SE)", 
  "Community Arm \n Mean (SE)",
  "Hybrid Arm \n Mean (SE)",
  "Women \n Mean (SE)", 
  "Men \n Mean (SE)",
  "Total \n Mean (SE)"
  )


  table_subset <- table_vars[table_vars$section=="D", ]
  
  tableDF <- data.frame(
        variable = character(),
        clinic_arm = character(),
        community_arm = character(),
        hybrid_arm = character(),
        Women = character(),
        Men = character(),
        Total = character()
    )
  
  
  for (v in unique(table_subset$var_name)) {
      
    data = ncd_merged_subset %>% filter(site == "AHRI") # subset to AHRI for this section
    
    m <- geeglm( get(v) ~ 1, 
            family = gaussian, data = data,
            id = hhid, corstr = "independence") 
    
    mean =  round( coef(m)[["(Intercept)"]], round_digits)
    se = round( summary(m)$coef["(Intercept)", 2], round_digits)
    
    result_total = paste0(mean, " (", se, ")")
    
    for (t in unique(data$arm)) {
        
      m <- geeglm( get(v) ~ 1, 
            family = gaussian, data = data %>% filter(arm == t),
            id = hhid, corstr = "independence") 
    
      mean = round( coef(m)[["(Intercept)"]], round_digits)
      se = round( summary(m)$coef["(Intercept)", 2], round_digits)
      
      assign(paste0("result_",t), paste0(mean, " (", se, ")"))
      
    }
    
     for (g in unique(data$genderR)) {
        
      m <- geeglm( get(v) ~ 1, 
            family = gaussian, data = data %>%  filter(genderR == g),
            id = hhid, corstr = "independence") 
    
      mean =  round(coef(m)[["(Intercept)"]], round_digits)
      se = round(summary(m)$coef["(Intercept)", 2], round_digits)
      
      assign(paste0("result_",g), paste0(mean, " (", se, ")"))
     }
    
    temp_row = c(table_vars[table_vars$var_name == v, "var_label"],
                 `result_Clinic arm` ,
                 `result_Community arm`,
                 `result_Hybrid arm`,
                 result_Women,
                 result_Men,
                 result_total)
    
    tableDF <- rbind(tableDF, temp_row)
}
  
  # Flextable
  
names(tableDF) <- c("variable", 
                   "clinic_arm", "community_arm", "hybrid_arm",
                   "Women", "Men", "Total")

ft <- flextable(tableDF) %>%
   
  delete_part(part = "header") %>%
  add_header_row(values = c(col_headings_mean))  %>%     
  align(i = 1, part = "header", align = "center") %>%
  width(width = 1.25) %>% 
    width(j = 1, width = 2) %>%
  theme_vanilla()  %>% 
  vline(j = c(1, 4, 6), border = fp_border_default(), part = "all")

flextable_to_rmd(ft)  

```

```{r, echo = F, include = F}

# NUMBER PLUGGING FOR MANUSCRIPT
## THIS IS VERY , VERY JANKY CODE - be careful!!

#Total

bmi = tableDF[[1,7]]
bmi_mean = as.numeric(substr(bmi, start = 1, stop = 4))
bmi_se = (as.numeric(substr(bmi, start = 7, stop = 10)))
lower = bmi_mean - qnorm(0.975)*bmi_se
upper = bmi_mean + qnorm(0.975)*bmi_se
round(lower, 2)
round(upper, 2)

sbp = tableDF[[2,7]]
sbp_mean = as.numeric(substr(sbp, start = 1, stop = 4))
sbp_se = (as.numeric(substr(sbp, start = 7, stop = 10)))
lower = sbp_mean - qnorm(0.975)*sbp_se
upper = sbp_mean + qnorm(0.975)*sbp_se
round(lower, 2)
round(upper, 2)

# Women

bmi = tableDF[[1,5]]
bmi_mean = as.numeric(substr(bmi, start = 1, stop = 4))
bmi_se = (as.numeric(substr(bmi, start = 7, stop = 10)))
lower = bmi_mean - qnorm(0.975)*bmi_se
upper = bmi_mean + qnorm(0.975)*bmi_se
round(lower, 2)
round(upper, 2)

sbp = tableDF[[2,5]]
sbp_mean = as.numeric(substr(sbp, start = 1, stop = 3)) # update start/stop manually
sbp_se = (as.numeric(substr(sbp, start = 6, stop = 9))) # update start/stop manually
lower = sbp_mean - qnorm(0.975)*sbp_se
upper = sbp_mean + qnorm(0.975)*sbp_se
round(lower, 1)
round(upper, 1)

# Men

bmi = tableDF[[1,6]]
bmi_mean = as.numeric(substr(bmi, start = 1, stop = 4))
bmi_se = (as.numeric(substr(bmi, start = 7, stop = 10)))
lower = bmi_mean - qnorm(0.975)*bmi_se
upper = bmi_mean + qnorm(0.975)*bmi_se
round(lower, 1)
round(upper, 1)

sbp = tableDF[[2,6]]
sbp_mean = as.numeric(substr(sbp, start = 1, stop = 4))
sbp_se = (as.numeric(substr(sbp, start = 7, stop = 10)))
lower = sbp_mean - qnorm(0.975)*sbp_se
upper = sbp_mean + qnorm(0.975)*sbp_se
round(lower, 1)
round(upper, 1)
```


### Page break

## Appendix Table 2: Descriptive statistics of cardiovascular risk in the DO ART study, by site (N = 1315)

&nbsp;


```{r, echo = F, warning = F, message = F, ft.split = T, ft.keepnext = F, results = 'asis'}
# Set up --------------------------------------------------------------------------

headings <- data.frame(
  section = c("A", "B", "C"),
  title = c( "", 
             "ii) Lifestyle and other risk",
              "iii) Cardiovascular Risk")
)

# A) Demographics
A_vars = c(
  "age_cat","genderR"
  )
A_var_labels = c(
  "Age", "Gender"
  )

# B) Lifestyle and Other Risk (same as above)

# C) Cardiovascular risk (same as above)

table_vars <- data.frame(
  
  var_name = c(A_vars, B_vars, C_vars),

  var_label = c(A_var_labels, B_var_labels, C_var_labels)) %>% 
  
  mutate( 
    
    section = case_when(
      var_name %in% c(A_vars) ~ "A",
      var_name %in% c(B_vars) ~ "B",
      var_name %in% c(C_vars) ~ "C")
    )
  

# Descriptive Proportion Table ----------------------------------------------------

col_headings_freq <- c(
  "Category",
  "SW Uganda \n n (%)",
  "Midlands KZN SA \n n (%)", 
  "Northern KZN SA \n n (%)",
  "Total \n n (%)"
  )


for (i in unique(headings$section)) {
  
  table_subset <- table_vars[table_vars$section==i, ]
  
  tableDF <- data.frame(
        variable = character(),
        category = character(),
        sw_uganda = character(),
        midlands_kzn = character(),
        northern_kzn = character(),
        Total = character()
    )
  
  for (v in unique(table_subset$var_name)) {
      
    data = ncd_merged_subset 
    
    temp <- data %>% 
      
      # Format table using Janitor package 
      tabyl(!!sym(v), site) %>% 
      adorn_totals(where = "col") %>% 
      adorn_percentages(denominator = "col") %>% 
      adorn_pct_formatting(digits = 0, affix_sign = TRUE) %>% 
      adorn_ns(position = "front") %>%
      as.data.frame() %>% 
      
      # Clean up headers
      rename(category = 1,
             sw_uganda = "ICOBI",
             midlands_kzn = "HSRC",
             northern_kzn = "AHRI") %>% 
      mutate(variable = table_vars[table_vars$var_name == v, "var_label"] ) %>% 
      select(variable, everything())
    
  tableDF <- rbind(tableDF, temp)
  
  }
  
  # Flextable

ft <- flextable(tableDF) %>%
  
  delete_part(part = "header") %>%
  add_header_row(values = c(headings[headings$section == i, "title"], col_headings_freq))  %>%     
  align(i = 1, part = "header", align = "center") %>%
  merge_v(j = "variable") %>%
  width(width = 1.55) %>%
  theme_vanilla() %>% 
  vline(j = c(2, 5), border = fp_border_default(), part = "all")

flextable_to_rmd(ft)  

rm(temp)  
}
```