---
title: "DO ART NCD Tables & Figures"
author: ""
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  word_document:
    reference_docx: word_styles.docx

---

```{r setup, include = F, echo = F, warning = F, message = F}

rm(list=ls())

# Load packages 

package.list <- c("plyr", "dplyr", "tidyr", "magrittr", "data.table", "ggplot2",
                  "janitor", "tables", "flextable", # table formatting
                  "geepack", "sandwich", # regression analysis 
                  "ggpubr"
                  )

# new.packages <- package.list[!(package.list %in% installed.packages()[,"Package"])]
# if(length(new.packages)) install.packages(new.packages)

invisible(lapply(package.list, library, character.only = TRUE))

# Load data

dir <- "C:/Users/msahu/Documents/Other_Research/DO_ART_NCD/"
in_dir <- paste0(dir, "0_data/3_cleaned_data/")

# Subset to South Africa only!!
# NOTE: we combine the community and hybrid arm (community follow-up), compared to clinic

ncd_merged_subset <- readRDS(paste0(in_dir, "ncd_merged_subset.rds")) %>% 
  filter(country == "South Africa") %>% 
  mutate(site = factor (site,
                       levels = c("HSRC",
                                  "AHRI"))) %>% 
  mutate(armR = case_when(arm == "Clinic arm" ~ "Clinic follow-up",
                          arm == "Community arm" ~ "Community follow-up",
                          arm == "Hybrid arm" ~ "Community follow-up" ))
  
  
round_digits = 2
p_digits = 3

# WARNING that chunks build on each other! Can't run individually

```

## Main paper tables (South Africa only)

+ Table 1: Descriptive statistics of cardiovascular risk in the South Africa site of the DO ART study, by trial arm and gender
+ Table 2: Poisson + linear regressions for community follow-up compared with clinic follow-up, and including VS
+ Table 3: Poisson + linear regressions with VS as predictor, stratified by treatment arm; with interaction term for VS

## Distribution figures (South Africa only)

+ Figure 1: CVD variables, comparing VS versus not

### Page Break

## Table 1: Descriptive statistics of cardiovascular risk in the South Africa site of the DO ART study, by trial arm and gender (N = 1010)

```{r, echo = F, warning = F, message = F, ft.split = T, ft.keepnext = F, results = 'asis'}

# Set up --------------------------------------------------------------------------

headings <- data.frame(
  section = c("A", "B", "C"),
  title = c( "", 
             "ii) Lifestyle and other risk",
              "iii) Cardiovascular Risk")
)

# A) Demographics
A_vars = c(
  "age_cat",
  "genderR"
  )
A_var_labels = c(
  "Age",
  "Gender"
  )

# B) Lifestyle and Other Risk

B_vars = c(  
  "smoking_cat",
  "exer_cat",
  "veg_cat",
  "stroke_cat")
B_var_labels = c(
  "Smoking Status  \n [Baseline]",
  "Days of exercise (per week) \n [Endline]",
  "Vegetable intake \n [Endline]",
   "Prior stroke or heart attack  \n [Endline]")


# C) Cardiovascular risk
C_vars = c(
  "bp_cat_exit", 
  "bmi_cat_exit", 
  "a1c_cat_exit", 
  "total_cholesterol_exit",
  "who_cvd_risk_exit")
C_var_labels = c(
  "Blood pressure \n [Endline]",
   "BMI (kg/m^2) \n [Endline]",
   "Hemoglobin A1C (%) \n [Endline]",
   "Total cholesterol (mg/dL) \n [Endline]",
   "10-year CVD risk score \n [Endline]")

table_vars <- data.frame(
  
  var_name = c(A_vars, B_vars, C_vars),

  var_label = c(A_var_labels, B_var_labels, C_var_labels)) %>% 
  
  mutate( 
    
    section = case_when(
      var_name %in% c(A_vars) ~ "A",
      var_name %in% c(B_vars) ~ "B",
      var_name %in% c(C_vars) ~ "C")
    )
  
# Descriptive Proportion Table ----------------------------------------------------

col_headings_freq <- c(
  "Category",
  "Clinic follow-up \n n (%)", 
  "Community follow-up \n n (%)",
  "Women \n n (%)",
  "Men \n n (%)",
  "Total \n n (%)"
  )

for (i in unique(headings$section)) {
  
  table_subset <- table_vars[table_vars$section==i, ]
  
  tableDF <- data.frame(
        variable = character(),
        category = character(),
        clinic_arm = character(),
        community_arm = character(),
        Women = character(),
        Men = character(),
        Total = character()
    )
  
  for (v in unique(table_subset$var_name)) {
      
    data = ncd_merged_subset
    
    temp1 <- data %>% 
      
      # Format table using Janitor package 
      tabyl(!!sym(v), armR) %>% 
      adorn_totals(where = "col") %>% 
      adorn_percentages(denominator = "col") %>% 
      adorn_pct_formatting(digits = 0, affix_sign = TRUE) %>% 
      adorn_ns(position = "front") %>%
      as.data.frame() %>% 
      
      # Clean up headers
      dplyr::rename(category = 1,
             clinic_arm = `Clinic follow-up`,
             community_arm = `Community follow-up`) %>% 
      mutate(variable = table_vars[table_vars$var_name == v, "var_label"] ) %>% 
      select(variable, category, clinic_arm, community_arm, Total)
    
    if (v != "genderR") {
    
    temp2 <- data %>% 
      
      # Format table using Janitor package 
      tabyl(!!sym(v), genderR) %>% 
      adorn_totals(where = "col") %>% 
      adorn_percentages(denominator = "col") %>% 
      adorn_pct_formatting(digits = 0, affix_sign = TRUE) %>% 
      adorn_ns(position = "front") %>%
      as.data.frame() %>% 
      
      # Clean up headers
      select(Women, Men)
    
    }
    
    if (v == "genderR") {
    
    temp2 <- data.frame(
      Women = "--",
      Men = "--"
    )
    
    }
  
  temp <- cbind(temp1, temp2) %>% 
    select(variable, category, clinic_arm, community_arm, Women, Men, Total)
      
  tableDF <- rbind(tableDF, temp)
  
  }
  
  # Flextable

ft <- flextable(tableDF) %>%
   
  delete_part(part = "header") %>%
  add_header_row(values = c(headings[headings$section == i, "title"], col_headings_freq))  %>%     
  align(i = 1, part = "header", align = "center") %>%
  merge_v(j = "variable") %>%
  width(width = 1.4) %>%
  theme_vanilla() %>% 
  vline(j = c(2, 4, 6), border = fp_border_default(), part = "all")

flextable_to_rmd(ft)  

rm(temp, temp1, temp2)  
}

```


### Page Break

## Table 2. Cardiovascular risk for community HIV follow-up care compared with clinic-based follow-up (N = 1010).

```{r, echo = F, warning = F, message = F, ft.split = T, ft.keepnext = F, results = 'asis'}

# Poisson REGRESSIONS --------------------------------------------------------------

reg_vars <- data.frame(
  
  var_name = c(
    "bp_hi_exit", 
    "overwt_exit", 
    "a1c_hi_exit",
   # "total_cholesterol_hi_exit",
    "smokingR"
),

  var_label = c(
    "Elevated BP",
    "Overweight (BMI >= 25)",
    "Elevated blood sugar (a1c >= 5.7)",
   # "Elevated lipids (total cholesterol >= 200)",
    "Smoker [baseline]"
    ))
  

regressionDF <- data.frame(
        variable = character(),
        rr = numeric(),
        rr_ci = character(),
        rr_p = numeric(),
        adj.rr = character(),
        adj.rr_ci = character(), 
        adj.rr_p = character(),
        ext.rr = character(),
        ext.rr_ci = character(), 
        ext.rr_p = character() 
    )

 
for (v in unique(reg_vars$var_name)) {
  
  # Adjusted for site only
  m <- geeglm(get(v) ~ armR + site, 
              family = poisson, data = ncd_merged_subset,
              id = hhid, corstr = "independence") 
  
  m.rr <- exp(coef(m)[["armRCommunity follow-up"]]) # Relative Risk
  m.se <- summary(m)$coef["armRCommunity follow-up",2] # SE
  m.rr_ci <- exp(c(coef(m)[["armRCommunity follow-up"]] - qnorm(0.975)*m.se, 
                  coef(m)[["armRCommunity follow-up"]] + qnorm(0.975)*m.se)) # RR: 95% CI with robust SE
  m.p <- summary(m)$coef["armRCommunity follow-up",4]

  # Adjusted for site, age, gender, smoking 
  
   if (v != "smokingR") {
  
  adj.m <- geeglm(get(v) ~ armR + site + age_cat + genderR + smoking_status, 
              family = poisson, data = ncd_merged_subset,
              id = hhid, corstr = "independence") 
  
   }
  
  if (v == "smokingR") {
  
  adj.m <- geeglm(get(v) ~ armR + site + age_cat + genderR, 
              family = poisson, data = ncd_merged_subset,
              id = hhid, corstr = "independence") 
  
   }
  
  adj.rr <- exp(coef(adj.m)[["armRCommunity follow-up"]]) # Relative Risk
  adj.se <- summary(adj.m)$coef["armRCommunity follow-up",2] # SE
  adj.rr_ci <- exp(c(coef(adj.m)[["armRCommunity follow-up"]] - qnorm(0.975)*adj.se, 
                  coef(adj.m)[["armRCommunity follow-up"]] + qnorm(0.975)*adj.se)) # RR: 95% CI with robust SE
  adj.p <- summary(adj.m)$coef["armRCommunity follow-up",4]

  # Adjusted for VS and site, age, gender, smoking 
  
  if (v != "smokingR") {
  
  ext.m <- geeglm(get(v) ~ armR + site + age_cat + genderR + smoking_status+ exit_viral_load_suppressedR, 
              family = poisson, data = ncd_merged_subset,
              id = hhid, corstr = "independence") 
  
  }
  
  if (v == "smokingR") {
    
  ext.m <- geeglm(get(v) ~ armR + site + age_cat + genderR + exit_viral_load_suppressedR, 
              family = poisson, data = ncd_merged_subset,
              id = hhid, corstr = "independence") 
  
  }
    
  ext.rr <- exp(coef(ext.m)[["armRCommunity follow-up"]]) # Relative Risk
  ext.se <- summary(ext.m)$coef["armRCommunity follow-up",2] # SE
  ext.rr_ci <- exp(c(coef(ext.m)[["armRCommunity follow-up"]] - qnorm(0.975)*ext.se, 
                  coef(ext.m)[["armRCommunity follow-up"]] + qnorm(0.975)*ext.se)) # RR: 95% CI with robust SE
  ext.p <- summary(ext.m)$coef["armRCommunity follow-up",4]
  
  # Bind
  
  temp_row <- c(reg_vars[reg_vars$var_name == v, "var_label"], 
                as.numeric(round(m.rr, round_digits)), 
                paste0("(",
                       as.numeric(round(m.rr_ci, round_digits))[1], 
                       ",",
                       as.numeric(round(m.rr_ci, round_digits))[2],
                       ")"),
                as.numeric(round(m.p, p_digits)),
                as.numeric(round(adj.rr, round_digits)), 
                paste0("(",
                       as.numeric(round(adj.rr_ci, round_digits))[1], 
                       ",",
                       as.numeric(round(adj.rr_ci, round_digits))[2],
                       ")"),
                as.numeric(round(adj.p, p_digits)),
                as.numeric(round(ext.rr, round_digits)), 
                paste0("(",
                       as.numeric(round(ext.rr_ci, round_digits))[1], 
                       ",",
                       as.numeric(round(ext.rr_ci, round_digits))[2],
                       ")"),
                as.numeric(round(ext.p, p_digits))
                )
  
  regressionDF <- rbind(regressionDF, temp_row)
  
}
  
names(regressionDF) =
  c("Variable",
    "Relative Risk",
    "95% CI",
    "p-value",
    "Adj. Relative Risk",
    "Adj. 95% CI",
    "Adj. p-value",
    "Ext. Relative Risk",
    "Ext. 95% CI",
    "Ext. p-value")


# Word Doc output
ft <- flextable(regressionDF) %>% 
  colformat_double(big.mark=",", digits = 1, na_str = "N/A") %>%
  add_header_row(values = c("", "Baseline Analysis", "Adjusted Analysis", "Extended Analysis (VS)"), 
                 top = T, colwidths = c(1, 3, 3, 3)) %>% 
  width(width = .94) %>%
  width(j = 1, width = 1.6) %>%
  theme_vanilla() %>% 
  vline(j = c(1, 4, 7), border = fp_border_default(), part = "all") %>% 
  align(i =1, align = "center", part = "header") 

ft

# LINEAR REGRESSIONS --------------------------------------------------------------

lin_reg_vars <- data.frame(
  
  var_name = c(
    "sbp_mean_exit",
    "dbp_mean_exit", 
    "bmi", 
    "hemoglobin_a1c_result",
    "lipid_result"),

  var_label = c(
    "Systolic BP (mmHg)",
    "Diastolic BP (mmHg)",
    "BMI (kg/m^2)",
    "Hemoglobin A1c (%)",
    "Total cholesterol (mg/dL)") 
)
  

regressionDF <- data.frame(
        variable = character(),
        rd = numeric(),
        rd_ci = character(),
        rd_p = numeric(),
        adj.rd = character(),
        adj.rd_ci = character(), 
        adj.rd_p = character(), 
        ext.rd = character(),
        ext.rd_ci = character(), 
        ext.rd_p = character()
    )

 
for (v in unique(lin_reg_vars$var_name)) {
 
  # Adjusted for site only
  lm <- geeglm(get(v) ~ armR + site, 
              family = gaussian, data = ncd_merged_subset,
              id = hhid, corstr = "independence") 
  rd <- coef(lm)[["armRCommunity follow-up"]] # Mean Difference
  lm.se <- summary(lm)$coef["armRCommunity follow-up",2] # SE
  rd_ci <- c(coef(lm)[["armRCommunity follow-up"]] - qnorm(0.975)*lm.se, 
                coef(lm)[["armRCommunity follow-up"]] + qnorm(0.975)*lm.se) # 95% CI
  rd_p <- summary(lm)$coef["armRCommunity follow-up",4]

  # Adjusted for site, age, gender, smoking 
  
  adj.lm <- geeglm(get(v) ~ armR + site + age_cat + genderR + smoking_status, 
              family = gaussian, data = ncd_merged_subset,
              id = hhid, corstr = "independence") 
  adj.rd <- coef(adj.lm)[["armRCommunity follow-up"]] # Mean Difference
  adj.lm.se <- summary(adj.lm)$coef["armRCommunity follow-up",2] # SE
  adj.rd_ci <- c(coef(adj.lm)[["armRCommunity follow-up"]] - qnorm(0.975)*adj.lm.se, 
                  coef(adj.lm)[["armRCommunity follow-up"]] + qnorm(0.975)*adj.lm.se) # 95% CI
  adj.rd_p <- summary(adj.lm)$coef["armRCommunity follow-up",4]

  # Adjusted for VS and site, age, gender, smoking 
  
  ext.lm <- geeglm(get(v) ~ armR + site + age_cat + genderR + smoking_status+ exit_viral_load_suppressedR, 
              family = gaussian, data = ncd_merged_subset,
              id = hhid, corstr = "independence") 
  ext.rd <- coef(ext.lm)[["armRCommunity follow-up"]] # Mean Difference
  ext.lm.se <- summary(ext.lm)$coef["armRCommunity follow-up",2] # SE
  ext.rd_ci <- c(coef(ext.lm)[["armRCommunity follow-up"]] - qnorm(0.975)*ext.lm.se, 
                  coef(ext.lm)[["armRCommunity follow-up"]] + qnorm(0.975)*ext.lm.se) # 95% CI
  ext.rd_p <- summary(ext.lm)$coef["armRCommunity follow-up",4]
 
  temp_row <- c(lin_reg_vars[lin_reg_vars$var_name == v, "var_label"], 
                as.numeric(round(rd, round_digits)), 
                paste0("(",
                       as.numeric(round(rd_ci, round_digits))[1], 
                       ",",
                       as.numeric(round(rd_ci, round_digits))[2],
                       ")"),
                as.numeric(round(rd_p, p_digits)),
                as.numeric(round(adj.rd, round_digits)), 
                paste0("(",
                       as.numeric(round(adj.rd_ci, round_digits))[1], 
                       ",",
                       as.numeric(round(adj.rd_ci, round_digits))[2],
                       ")"),
                as.numeric(round(adj.rd_p, p_digits)),
                as.numeric(round(ext.rd, round_digits)), 
                paste0("(",
                       as.numeric(round(ext.rd_ci, round_digits))[1], 
                       ",",
                       as.numeric(round(ext.rd_ci, round_digits))[2],
                       ")"),
                as.numeric(round(ext.rd_p, p_digits))
                )
  
  regressionDF <- rbind(regressionDF, temp_row)
  
}
  
names(regressionDF) =
  c("Variable",
    "Mean Difference",
    "95% CI",
    "p-value",
    "Adj. Mean Difference",
    "Adj. 95% CI",
    "Adj. p-value",
    "Ext. Mean Difference",
    "Ext. 95% CI",
    "Ext. p-value")

# Word Doc output
ft <- flextable(regressionDF) %>% 
  colformat_double(big.mark=",", digits = 1, na_str = "N/A") %>%
  add_header_row(values = c("", "Baseline Analysis", "Adjusted Analysis", "Extended Analysis (VS)"), 
                 top = T, colwidths = c(1, 3, 3, 3)) %>% 
  width(width = .94) %>%
  width(j = 1, width = 1.6) %>%
  theme_vanilla()  %>% 
  vline(j = c(1, 4, 7), border = fp_border_default(), part = "all") %>% 
  align(i =1, align = "center", part = "header") 

ft

```

&nbsp;

+ Relative risk is estimated using a GEE poisson model (and log link).
+ Mean Difference is estimated using a GEE linear model.
+ Baseline model adjusts for site only
+ Adjusted models includes site, age, smoking and gender.
+ Extended model includes model endline viral suppression [binary] plus all adjustment variables

### Page Break

## Table 3: Poisson + linear regressions with VS as predictor, stratified by treatment arm; with interaction term for VS 

```{r, echo = F, warning = F, message = F, ft.split = T, ft.keepnext = F, results = 'asis'}

vs_subset <- ncd_merged_subset %>% 
  filter(!is.na(exit_viral_load_result))

# POISSON REGRESSIONS -------------------------------------------------------------

reg_vars <- data.frame(
  
  var_name = c(
    "bp_hi_exit", 
    "overwt_exit", 
    "a1c_hi_exit",
  #  "total_cholesterol_hi_exit",
    "smokingR"),

  var_label = c(
    "Elevated BP",
    "Overweight (BMI >= 25)",
    "Elevated blood sugar (a1c >= 5.7)",
 #   "Elevated lipids (total cholesterol >= 200)",
    "Current smoker [baseline]"))
  

# COMMUNITY VS. CLINIC FOLLOW-UP

# --- clinic

vs_arm_subset <- vs_subset %>% filter(armR == "Clinic follow-up")

N_clinic = vs_arm_subset %>% nrow()

regressionDF_clinic <- data.frame(
        variable = character(),
        clinic_adj.rr =  numeric(),
        clinic_adj.rr_ci = character(), 
        clinic_adj.rr_p = character()
    )
 
for (v in unique(reg_vars$var_name)) {


  # Adjusted for site, age, gender, smoking 
  
  if (v != "smokingR") {
  
  adj.m <- geeglm(get(v) ~ exit_viral_load_suppressed + site + age_cat + genderR + smokingR, 
              family = poisson, data = vs_arm_subset,
              id = hhid, corstr = "independence") 
  }
  
  if (v == "smokingR") {
  
  adj.m <- geeglm(get(v) ~ exit_viral_load_suppressed + site + age_cat + genderR, 
              family = poisson, data = vs_arm_subset,
              id = hhid, corstr = "independence") 
  }
  
  adj.rr <- exp(coef(adj.m)[["exit_viral_load_suppressedTRUE"]]) # Relative Risk
  adj.se <- summary(adj.m)$coef["exit_viral_load_suppressedTRUE",2] # SE
  adj.rr_ci <- exp(c(coef(adj.m)[["exit_viral_load_suppressedTRUE"]] - qnorm(0.975)*adj.se, 
                  coef(adj.m)[["exit_viral_load_suppressedTRUE"]] + qnorm(0.975)*adj.se)) # RR: 95% CI 
  adj.p <- summary(adj.m)$coef["exit_viral_load_suppressedTRUE",4]
  
  
  temp_row <- c(reg_vars[reg_vars$var_name == v, "var_label"], 
                as.numeric(round(adj.rr, round_digits)), 
                paste0("(",
                       as.numeric(round(adj.rr_ci, round_digits))[1], 
                       ",",
                       as.numeric(round(adj.rr_ci, round_digits))[2],
                       ")"),
                as.numeric(round(adj.p, p_digits)))
  
  regressionDF_clinic <- rbind(regressionDF_clinic, temp_row) %>% 
    rename(variable = 1)
  
}
  
# --- community

vs_arm_subset <- vs_subset %>% filter(armR == "Community follow-up")

N_community = vs_arm_subset %>% nrow()

regressionDF_community <- data.frame(
        variable = character(),
        community_adj.rr =  numeric(),
        community_adj.rr_ci = character(), 
        community_adj.rr_p = character()
    )
 
for (v in unique(reg_vars$var_name)) {

  # Adjusted for site, age, gender, smoking 
  
  if (v != "smokingR") {
  
  adj.m <- geeglm(get(v) ~ exit_viral_load_suppressed + site + age_cat + genderR + smokingR, 
              family = poisson, data = vs_arm_subset,
              id = hhid, corstr = "independence") 
  }
  
  if (v == "smokingR") {
  
  adj.m <- geeglm(get(v) ~ exit_viral_load_suppressed + site + age_cat + genderR, 
              family = poisson, data = vs_arm_subset,
              id = hhid, corstr = "independence") 
  }
  
  adj.rr <- exp(coef(adj.m)[["exit_viral_load_suppressedTRUE"]]) # Relative Risk
  adj.se <- summary(adj.m)$coef["exit_viral_load_suppressedTRUE",2] # SE
  adj.rr_ci <- exp(c(coef(adj.m)[["exit_viral_load_suppressedTRUE"]] - qnorm(0.975)*adj.se, 
                  coef(adj.m)[["exit_viral_load_suppressedTRUE"]] + qnorm(0.975)*adj.se)) # RR: 95% CI 
  adj.p <- summary(adj.m)$coef["exit_viral_load_suppressedTRUE",4]
  
  
  temp_row <- c(reg_vars[reg_vars$var_name == v, "var_label"], 
                as.numeric(round(adj.rr, round_digits)), 
                paste0("(",
                       as.numeric(round(adj.rr_ci, round_digits))[1], 
                       ",",
                       as.numeric(round(adj.rr_ci, round_digits))[2],
                       ")"),
                as.numeric(round(adj.p, p_digits)))
  
  regressionDF_community <- rbind(regressionDF_community, temp_row) %>% 
    rename(variable = 1)
  
}

# Interaction term: Adjusted for site, age, gender, smoking 

intDF <- data.frame(
        variable = character(),
        int.p = character()
    )
 
for (v in unique(reg_vars$var_name)) {

  
  if (v != "smokingR") {
  
  int.m <- geeglm(get(v) ~ site + age_cat + genderR + smoking_status + exit_viral_load_suppressed*armR, 
              family = poisson, data = vs_subset,
              id = hhid, corstr = "independence") 
  int.p <- summary(int.m)$coef["exit_viral_load_suppressedTRUE:armRCommunity follow-up",4]
  
  }
  
  if (v == "smokingR") {
  
  int.m <- geeglm(get(v) ~ site + age_cat + genderR + exit_viral_load_suppressed*armR, 
              family = poisson, data = vs_subset,
              id = hhid, corstr = "independence") 

  int.p <- summary(int.m)$coef["exit_viral_load_suppressedTRUE:armRCommunity follow-up",4]
  
  }
   temp_row <- c(reg_vars[reg_vars$var_name == v, "var_label"], 
                as.numeric(round(int.p, p_digits)))
  
  intDF <- rbind(intDF, temp_row) %>% 
    rename(variable = 1)
  
  }


regressionDF <- regressionDF_clinic %>% 
  left_join(regressionDF_community, by = "variable") %>% 
  left_join(intDF, by = "variable")
  
names(regressionDF) =
  c("Variable",
    "Adj. Relative Risk",
    "Adj. 95% CI",
    "Adj. p-value",
    "Adj. Relative Risk ",
    "Adj. 95% CI ",
    "Adj. p-value ",
    "Adj.  p-value")


# Word Doc output
ft <- flextable(regressionDF) %>% 
  colformat_double(big.mark=",", digits = 1, na_str = "N/A") %>%
  add_header_row(values = c("", paste0("Clinic follow-up, Adjusted \n (N = ", N_clinic, ")"),
                            paste0("Community follow-up, Adjusted \n (N = ", N_community, ")"), 
                             paste0("Interaction \n (N = ", N_community + N_clinic, ")")), 
                 top = T, colwidths = c(1, 3, 3, 1)) %>% 
  width(width = .94) %>%
  width(j = 1, width = 1.6) %>%
  theme_vanilla()  %>% 
  vline(j = c(1, 4, 7), border = fp_border_default(), part = "all") %>% 
  align(i =1, align = "center", part = "header") 

ft

# LINEAR REGRESSIONS -----------------------------------------------------------------

lin_reg_vars <- data.frame(
  
  var_name = c(
    "sbp_mean_exit",
    "dbp_mean_exit", 
    "bmi", 
    "hemoglobin_a1c_result",
    "lipid_result"),

  var_label = c(
    "Systolic BP (mmHg)",
    "Diastolic BP (mmHg)",
    "BMI (kg/m^2)",
    "Hemoglobin A1c (%)",
    "Total cholesterol (mg/dL)") 
)
  


# COMMUNITY VS. CLINIC FOLLOW-UP

# --- clinic

vs_arm_subset <- vs_subset %>% filter(armR == "Clinic follow-up")

N_clinic = vs_arm_subset %>% nrow()

regressionDF_clinic <- data.frame(
        variable = character(),
        clinic_adj.rr =  numeric(),
        clinic_adj.rr_ci = character(), 
        clinic_adj.rr_p = character()
    )
 
for (v in unique(lin_reg_vars$var_name)) {

  # Adjusted for site, age, gender, smoking 
  
  adj.lm <- geeglm(get(v) ~ exit_viral_load_suppressed + site + age_cat + genderR + smokingR, # NOTE THIS SMOKING VARIABLE IS DIFFERENT
              family = gaussian, data = vs_arm_subset,
              id = hhid, corstr = "independence") 
  adj.rd <- coef(adj.lm)[["exit_viral_load_suppressedTRUE"]] # Mean Difference
  adj.lm.se <- summary(adj.lm)$coef["exit_viral_load_suppressedTRUE",2] # SE
  adj.rd_ci <- c(coef(adj.lm)[["exit_viral_load_suppressedTRUE"]] - qnorm(0.975)*adj.lm.se, 
                  coef(adj.lm)[["exit_viral_load_suppressedTRUE"]] + qnorm(0.975)*adj.lm.se) # 95% CI
  adj.rd_p <- summary(adj.lm)$coef["exit_viral_load_suppressedTRUE",4]
 

  temp_row <- c(lin_reg_vars[lin_reg_vars$var_name == v, "var_label"], 
                as.numeric(round(adj.rd, round_digits)), 
                paste0("(",
                       as.numeric(round(adj.rd_ci, round_digits))[1], 
                       ",",
                       as.numeric(round(adj.rd_ci, round_digits))[2],
                       ")"),
                as.numeric(round(adj.rd_p, p_digits)))
  
  regressionDF_clinic <- rbind(regressionDF_clinic, temp_row) %>% 
    rename(variable = 1)
  
}

# --- ccommunity

vs_arm_subset <- vs_subset %>% filter(armR == "Community follow-up")

N_community = vs_arm_subset %>% nrow()

regressionDF_community <- data.frame(
        variable = character(),
        community_adj.rr =  numeric(),
        community_adj.rr_ci = character(), 
        community_adj.rr_p = character()
    )
 
for (v in unique(lin_reg_vars$var_name)) {

  # Adjusted for site, age, gender, smoking 
  
  adj.lm <- geeglm(get(v) ~ exit_viral_load_suppressed + site + age_cat + genderR + smokingR, # NOTE THIS SMOKING VARIABLE IS DIFFERENT
              family = gaussian, data = vs_arm_subset,
              id = hhid, corstr = "independence") 
  adj.rd <- coef(adj.lm)[["exit_viral_load_suppressedTRUE"]] # Mean Difference
  adj.lm.se <- summary(adj.lm)$coef["exit_viral_load_suppressedTRUE",2] # SE
  adj.rd_ci <- c(coef(adj.lm)[["exit_viral_load_suppressedTRUE"]] - qnorm(0.975)*adj.lm.se, 
                  coef(adj.lm)[["exit_viral_load_suppressedTRUE"]] + qnorm(0.975)*adj.lm.se) # 95% CI
  adj.rd_p <- summary(adj.lm)$coef["exit_viral_load_suppressedTRUE",4]
 

  temp_row <- c(lin_reg_vars[lin_reg_vars$var_name == v, "var_label"], 
                as.numeric(round(adj.rd, round_digits)), 
                paste0("(",
                       as.numeric(round(adj.rd_ci, round_digits))[1], 
                       ",",
                       as.numeric(round(adj.rd_ci, round_digits))[2],
                       ")"),
                as.numeric(round(adj.rd_p, p_digits)))
  
  regressionDF_community <- rbind(regressionDF_community, temp_row) %>% 
    rename(variable = 1)
  
}  



intDF <- data.frame(
        variable = character(),
        int.p = character()
    )
 
for (v in unique(lin_reg_vars$var_name)) {
  
  int.m <- geeglm(get(v) ~  site + age_cat + genderR + smoking_status + exit_viral_load_suppressed*armR, 
              family = gaussian, data = vs_subset,
              id = hhid, corstr = "independence") 
  int.p <- summary(int.m)$coef["exit_viral_load_suppressedTRUE:armRCommunity follow-up",4]
  
 
  temp_row <- c(lin_reg_vars[lin_reg_vars$var_name == v, "var_label"], 
                as.numeric(round(int.p, p_digits)))
  
  intDF <- rbind(intDF, temp_row) %>% 
    rename(variable = 1)
  
  }


regressionDF <- regressionDF_clinic %>% 
  left_join(regressionDF_community, by = "variable") %>% 
  left_join(intDF, by = "variable")
  
names(regressionDF) =
  c("Variable",
    "Adj. Relative Risk",
    "Adj. 95% CI",
    "Adj. p-value",
    "Adj. Relative Risk ",
    "Adj. 95% CI ",
    "Adj. p-value ",
    "Adj.  p-value")


# Word Doc output
ft <- flextable(regressionDF) %>% 
  colformat_double(big.mark=",", digits = 1, na_str = "N/A") %>%
  add_header_row(values = c("", paste0("Clinic follow-up, Adjusted \n (N = ", N_clinic, ")"),
                            paste0("Community follow-up, Adjusted \n (N = ", N_community, ")"), 
                             paste0("Interaction \n (N = ", N_community + N_clinic, ")")), 
                 top = T, colwidths = c(1, 3, 3, 1)) %>% 
  width(width = .94) %>%
  width(j = 1, width = 1.6) %>%
  theme_vanilla()  %>% 
  vline(j = c(1, 4, 7), border = fp_border_default(), part = "all") %>% 
  align(i =1, align = "center", part = "header") 

ft

```
&nbsp;
+ Note, we drop 27 participants without endline viral load available.
+ Relative risk is estimated using a GEE poisson model (and log link).
+ Mean Difference is estimated using a GEE linear model.
+ Adjusted models includes site, age, smoking and gender.
+ The p-value for interaction term comes from the adjusted model with an interaction term between viral suppression and trial arm
+ For smoker, the adjusted and extended analyses do not adjust for smoking

### Page Break
## Figure 1: Distribution, by viral suppression status at endline [dashed lines are group medians]

```{r, echo = F, fig.height = 3.4, fig.width = 10, warning = F, message = F, results = 'hide'}
df = ncd_merged_subset %>%  filter(exit_viral_load_suppressedR != "Missing")
alpha_level = 0.5
lp = "bottom" # legend position, for all distribution figures

# Excluding missing

vs_colors = c("#00A08A", "#FF0000")
vs_title = "Virally suppressed at exit"

# SBP        

cvd_cutoff1 = 120
cvd_cutoff2 = NA
cvd_label = "Systolic BP (mmHg)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(sbp_mean_exit, na.rm = T))
                
p1 <-  ggplot(df, aes(x = sbp_mean_exit, fill = exit_viral_load_suppressedR)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values = vs_colors) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values= vs_colors) +
      guides(fill=guide_legend(title = vs_title)) +
      guides(color=guide_legend(title = vs_title)) +
      theme_bw() +
      theme(legend.position = lp)
    
# DBP

cvd_cutoff1 = 80
cvd_cutoff2 = NA
cvd_label = "Diastolic BP (mmHg)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(dbp_mean_exit, na.rm = T))
                
p2 <-  ggplot(df, aes(x = dbp_mean_exit, fill = exit_viral_load_suppressedR)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values= vs_colors) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values= vs_colors) +
      guides(fill=guide_legend(title=vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw() +
      theme(legend.position = lp)

# BMI

cvd_cutoff1 = 25
cvd_cutoff2 = 30
cvd_label = "BMI (kg/m^2)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(bmi, na.rm = T))
                
p3 <-  ggplot(df, aes(x = bmi, fill = exit_viral_load_suppressedR)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values = vs_colors) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values = vs_colors) +
      guides(fill=guide_legend(title=vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw() +
      theme(legend.position = lp)

# A1c

cvd_cutoff1 = 5.7
cvd_cutoff2 = 6.5
cvd_label = "Hemoglobin A1c (%)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(hemoglobin_a1c_result, na.rm = T))
                
p4 <-  ggplot(df, aes(x = hemoglobin_a1c_result, fill = exit_viral_load_suppressedR)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values = vs_colors) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values = vs_colors) +
      guides(fill=guide_legend(title=vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw() +
      theme(legend.position = lp)

# Cholesterol


cvd_cutoff1 = 200
cvd_cutoff2 = 240
cvd_label = "Total cholesterol (mg/dL)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(lipid_result, na.rm = T))
                
p5 <-  ggplot(df, aes(x = lipid_result, fill = exit_viral_load_suppressedR)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values = vs_colors) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values = vs_colors) +
      guides(fill=guide_legend(title=vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw() +
      theme(legend.position = lp)

# Arrange!

ggarrange(p1, p3, p4, p5, # skip DBP
          ncol = 2)


```
