---
title: "DO ART NCD Supplement"
author: ""
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  word_document:
    reference_docx: word_styles.docx

---

```{r setup, include = F, echo = F, warning = F, message = F}

rm(list=ls())

# Load packages

package.list <- c("plyr", "dplyr", "tidyr", "magrittr", "data.table", "ggplot2",
                  "janitor", "tables", "flextable", # table formatting
                  "geepack", "sandwich", # regression analysis 
                  "ggpubr"
                  )

invisible(lapply(package.list, library, character.only = TRUE))

# Load data

dir <- "C:/Users/msahu/Documents/Other_Research/DO_ART_NCD/"
in_dir <- paste0(dir, "0_data/3_cleaned_data/")


ncd_merged_subset <- readRDS(paste0(in_dir, "ncd_merged_subset.rds")) %>% 
  mutate(armR = case_when(arm == "Clinic arm" ~ "Clinic follow-up",
                          arm == "Community arm" ~ "Community follow-up",
                          arm == "Hybrid arm" ~ "Community follow-up" ))



ncd_noHybrid <- ncd_merged_subset %>% filter(arm!= "Hybrid arm")
round_digits = 2
p_digits = 3

```


# Appendix tables 

## S1: Variables Description

+ S1 Codebook (included with main paper)

## S2: Additional Descriptive Statistics

+ S2, Table 1: Change in cardiovascular risk from baseline to endline, by trial arm and gender (AHRI site only, N = 350)
+ S2, Table 2: Descriptive statistics of cardiovascular risk in the DO ART study, by site and including Uganda (N = 1315) 

## S3: Additional Analysis

+ S3, Table 1: Table 3 for clinic arm (unadjusted and adjusted)
+ S3, Table 2: Table 3 for community arm (unadjusted and adjusted)
+ S3, Table 3: Interaction term coefficients 

## S4: Figures

+ S4 Figure 1: CVD variables, comparing community follow-up with clinic follow-up
+ S4 Figure 2: Distribution of cardiovascular risk, by viral suppression status at exit 
+ S4 Figure 3: CVD variables, comparing VS versus not - CLINIC FOLLOW-UP GROUP
+ S4 Figure 4: CVD variables, comparing VS versus not - COMMUNITY FOLLOW-UP GROUP
+ S4 Figure 5: CVD variables, by age 

## Number plugging (rough)

### Page Break


## Appendix Table 1: Change in cardiovascular risk from baseline to endline, by trial arm and gender (AHRI site only, N = 350)

&nbsp;


```{r, echo = F, warning = F, message = F, ft.split = T, ft.keepnext = F, results = 'asis'}
  
# Set up -------------------------------------------------------------

headings <- data.frame(
  section = c("A", "B", "C"),
  title = c( "", 
             "ii) Lifestyle and other risk",
              "iii) Cardiovascular Risk")
)

# A) Demographics
A_vars = c(
  "age_cat",
  "genderR"
  )
A_var_labels = c(
  "Age",
  "Gender"
  )

# B) Lifestyle and Other Risk

B_vars = c(  
  "smoking_cat",
  "exer_cat",
  "veg_cat",
  "stroke_cat")
B_var_labels = c(
  "Smoking Status  \n [Baseline]",
  "Days of exercise (per week) \n [Endline]",
  "Vegetable intake \n [Endline]",
   "Prior stroke or heart attack  \n [Endline]")


# C) Cardiovascular risk
C_vars = c(
  "bp_cat_exit", 
  "bmi_cat_exit", 
  "a1c_cat_exit", 
  "total_cholesterol_exit",
  "who_cvd_risk_exit")
C_var_labels = c(
  "Blood pressure \n [Endline]",
   "BMI (kg/m^2) \n [Endline]",
   "Hemoglobin A1C (%) \n [Endline]",
   "Total cholesterol (mg/dL) \n [Endline]",
   "10-year CVD risk score \n [Endline]")

# D) Change in CVD risk
D_vars = c(  
  "bmi_diff",
  "sbp_diff")
D_var_labels = c(
  "Change in BMI, baseline to endline  \n [AHRI only]",
  "Change in Systolic Blood pressure, baseline to endline  \n [AHRI only]" )


table_vars <- data.frame(
  
  var_name = c(D_vars),

  var_label = c(D_var_labels)) %>% 
  
  mutate( 
    
    section = case_when(
      var_name %in% c(D_vars) ~ "D"))
  
  
# Descriptive Proportion Table ----------------------------------------------------

col_headings_mean <- c(
  "Change in CVD risk",
  "Clinic Follow-Up Arm \n Mean (SE)", 
  "Community Follow-Up Arm \n Mean (SE)",
  "Women \n Mean (SE)", 
  "Men \n Mean (SE)",
  "Total \n Mean (SE)"
  )


  table_subset <- table_vars[table_vars$section=="D", ]
  
  tableDF <- data.frame(
        variable = character(),
        clinic_arm = character(),
        community_arm = character(),
        hybrid_arm = character(),
        Women = character(),
        Men = character(),
        Total = character()
    )
  
  
  for (v in unique(table_subset$var_name)) {
      
    data = ncd_merged_subset %>% filter(site == "AHRI") # subset to AHRI for this section
    
    m <- geeglm( get(v) ~ 1, 
            family = gaussian, data = data,
            id = hhid, corstr = "independence") 
    
    mean =  round( coef(m)[["(Intercept)"]], round_digits)
    se = round( summary(m)$coef["(Intercept)", 2], round_digits)
    
    result_total = paste0(mean, " (", se, ")")
    
    for (t in unique(data$armR)) {
        
      m <- geeglm( get(v) ~ 1, 
            family = gaussian, data = data %>% filter(armR == t),
            id = hhid, corstr = "independence") 
    
      mean = round( coef(m)[["(Intercept)"]], round_digits)
      se = round( summary(m)$coef["(Intercept)", 2], round_digits)
      
      assign(paste0("result_",t), paste0(mean, " (", se, ")"))
      
    }
    
     for (g in unique(data$genderR)) {
        
      m <- geeglm( get(v) ~ 1, 
            family = gaussian, data = data %>%  filter(genderR == g),
            id = hhid, corstr = "independence") 
    
      mean =  round(coef(m)[["(Intercept)"]], round_digits)
      se = round(summary(m)$coef["(Intercept)", 2], round_digits)
      
      assign(paste0("result_",g), paste0(mean, " (", se, ")"))
     }
    
    temp_row = c(table_vars[table_vars$var_name == v, "var_label"],
                 `result_Clinic follow-up` ,
                 `result_Community follow-up`,
                 result_Women,
                 result_Men,
                 result_total)
    
    tableDF <- rbind(tableDF, temp_row)
}
  
  # Flextable
  
names(tableDF) <- c("variable", 
                   "clinic_arm", "community_arm",
                   "Women", "Men", "Total")

ft <- flextable(tableDF) %>%
   
  delete_part(part = "header") %>%
  add_header_row(values = c(col_headings_mean))  %>%     
  align(i = 1, part = "header", align = "center") %>%
  width(width = 1.25) %>% 
    width(j = 1, width = 2) %>%
  theme_vanilla()  %>% 
  vline(j = c(1, 3, 5), border = fp_border_default(), part = "all")

flextable_to_rmd(ft)  

```



### Page break

## Appendix Table 2: Descriptive statistics of cardiovascular risk in the DO ART study, by site (N = 1315)

&nbsp;


```{r, echo = F, warning = F, message = F, ft.split = T, ft.keepnext = F, results = 'asis'}
# Set up --------------------------------------------------------------------------

headings <- data.frame(
  section = c("A", "B", "C"),
  title = c( "", 
             "ii) Lifestyle and other risk",
              "iii) Cardiovascular Risk")
)

# A) Demographics
A_vars = c(
  "age_cat","genderR"
  )
A_var_labels = c(
  "Age", "Gender"
  )

# B) Lifestyle and Other Risk (same as above)

# C) Cardiovascular risk (same as above)

table_vars <- data.frame(
  
  var_name = c(A_vars, B_vars, C_vars),

  var_label = c(A_var_labels, B_var_labels, C_var_labels)) %>% 
  
  mutate( 
    
    section = case_when(
      var_name %in% c(A_vars) ~ "A",
      var_name %in% c(B_vars) ~ "B",
      var_name %in% c(C_vars) ~ "C")
    )
  

# Descriptive Proportion Table ----------------------------------------------------

col_headings_freq <- c(
  "Category",
  "SW Uganda \n n (%)",
  "Midlands KZN SA \n n (%)", 
  "Northern KZN SA \n n (%)",
  "Total \n n (%)"
  )


for (i in unique(headings$section)) {
  
  table_subset <- table_vars[table_vars$section==i, ]
  
  tableDF <- data.frame(
        variable = character(),
        category = character(),
        sw_uganda = character(),
        midlands_kzn = character(),
        northern_kzn = character(),
        Total = character()
    )
  
  for (v in unique(table_subset$var_name)) {
      
    data = ncd_merged_subset 
    
    temp <- data %>% 
      
      # Format table using Janitor package 
      tabyl(!!sym(v), site) %>% 
      adorn_totals(where = "col") %>% 
      adorn_percentages(denominator = "col") %>% 
      adorn_pct_formatting(digits = 0, affix_sign = TRUE) %>% 
      adorn_ns(position = "front") %>%
      as.data.frame() %>% 
      
      # Clean up headers
      rename(category = 1,
             sw_uganda = "ICOBI",
             midlands_kzn = "HSRC",
             northern_kzn = "AHRI") %>% 
      mutate(variable = table_vars[table_vars$var_name == v, "var_label"] ) %>% 
      select(variable, everything())
    
  tableDF <- rbind(tableDF, temp)
  
  }
  
  # Flextable

ft <- flextable(tableDF) %>%
  
  delete_part(part = "header") %>%
  add_header_row(values = c(headings[headings$section == i, "title"], col_headings_freq))  %>%     
  align(i = 1, part = "header", align = "center") %>%
  merge_v(j = "variable") %>%
  width(width = 1.55) %>%
  theme_vanilla() %>% 
  vline(j = c(2, 5), border = fp_border_default(), part = "all")

flextable_to_rmd(ft)  

rm(temp)  
}
```

&nbsp;

### Page break

## Appendix S3, Table 1: Cardiovascular risk among people virally suppressed versus those not virally suppressed at endline, in the clinic-based follow-up arm (N = 341).

```{r, echo = F, warning = F, message = F, ft.split = T, ft.keepnext = F, results = 'asis'}

# Subset to South Africa only and clinic arm only!

ncd_merged_subset <- readRDS(paste0(in_dir, "ncd_merged_subset.rds")) %>% 
  filter(country == "South Africa") %>% 
  mutate(site = factor (site,
                       levels = c("HSRC",
                                  "AHRI"))) %>% 
  mutate(armR = case_when(arm == "Clinic arm" ~ "Clinic follow-up",
                          arm == "Community arm" ~ "Community follow-up",
                          arm == "Hybrid arm" ~ "Community follow-up" )) %>% 
  filter(armR == "Clinic follow-up")
  
  
round_digits = 2
p_digits = 3

# DROP NA for GEE to run

vs_subset <- ncd_merged_subset %>% 
  filter(!is.na(exit_viral_load_result))

# POISSON REGRESSIONS --------------------------------------------------------------------------

reg_vars <- data.frame(
  
  var_name = c(
    "bp_hi_exit", 
    "overwt_exit", 
    "a1c_hi_exit",
    "smokingR"
   ),

  var_label = c(
    "Elevated BP",
    "Overweight (BMI >= 25)",
    "Elevated blood sugar (a1c >= 5.7)",
    "Current smoker [baseline]"
  ))
  
regressionDF <- data.frame(
        variable = character(),
        rr = numeric(),
        rr_ci = character(),
        rr_p = numeric(),
        adj.rr = character(),
        adj.rr_ci = character(), 
        adj.rr_p = character() 
    )

 
for (v in unique(reg_vars$var_name)) {

  # Adjusted for site only
  m <- geeglm(get(v) ~ site + exit_viral_load_suppressed, 
              family = poisson, data = vs_subset,
              id = hhid, corstr = "independence") 
  m.rr <- exp(coef(m)[["exit_viral_load_suppressedTRUE"]]) # Relative Risk
  m.se <- summary(m)$coef["exit_viral_load_suppressedTRUE",2] # SE
  m.rr_ci <- exp(c(coef(m)[["exit_viral_load_suppressedTRUE"]] - qnorm(0.975)*m.se, 
                  coef(m)[["exit_viral_load_suppressedTRUE"]] + qnorm(0.975)*m.se)) # RR: 95% CI 
  m.p <- summary(m)$coef["exit_viral_load_suppressedTRUE",4]
  
  # Adjusted for site, age, gender, smoking 
  
  if (v != "smokingR") {
  
  adj.m <- geeglm(get(v) ~ site + age_cat + genderR + smokingR + exit_viral_load_suppressed, 
              family = poisson, data = vs_subset,
              id = hhid, corstr = "independence") 
  
  adj.rr <- exp(coef(adj.m)[["exit_viral_load_suppressedTRUE"]]) # Relative Risk
  adj.se <- summary(adj.m)$coef["exit_viral_load_suppressedTRUE",2] # SE
  adj.rr_ci <- exp(c(coef(adj.m)[["exit_viral_load_suppressedTRUE"]] - qnorm(0.975)*adj.se, 
                  coef(adj.m)[["exit_viral_load_suppressedTRUE"]] + qnorm(0.975)*adj.se)) # RR: 95% CI with robust SE
  adj.p <- summary(adj.m)$coef["exit_viral_load_suppressedTRUE",4]
  
  }
  
  if (v == "smokingR") {
  
  adj.m <- geeglm(get(v) ~ site + age_cat + genderR + exit_viral_load_suppressed, 
              family = poisson, data = vs_subset,
              id = hhid, corstr = "independence") 
  
  adj.rr <- exp(coef(adj.m)[["exit_viral_load_suppressedTRUE"]]) # Relative Risk
  adj.se <- summary(adj.m)$coef["exit_viral_load_suppressedTRUE",2] # SE
  adj.rr_ci <- exp(c(coef(adj.m)[["exit_viral_load_suppressedTRUE"]] - qnorm(0.975)*adj.se, 
                  coef(adj.m)[["exit_viral_load_suppressedTRUE"]] + qnorm(0.975)*adj.se)) # RR: 95% CI with robust SE
  adj.p <- summary(adj.m)$coef["exit_viral_load_suppressedTRUE",4]
  
  }
  
  temp_row <- c(reg_vars[reg_vars$var_name == v, "var_label"], 
                as.numeric(round(m.rr, round_digits)), 
                paste0("(",
                       as.numeric(round(m.rr_ci, round_digits))[1], 
                       ",",
                       as.numeric(round(m.rr_ci, round_digits))[2],
                       ")"),
                as.numeric(round(m.p, p_digits)),
                as.numeric(round(adj.rr, round_digits)), 
                paste0("(",
                       as.numeric(round(adj.rr_ci, round_digits))[1], 
                       ",",
                       as.numeric(round(adj.rr_ci, round_digits))[2],
                       ")"),
                as.numeric(round(adj.p, p_digits)))
  
  regressionDF <- rbind(regressionDF, temp_row)
  
}
  
names(regressionDF) =
  c("Variable",
    "Relative Risk",
    "95% CI",
    "p-value",
    "Adj. Relative Risk",
    "Adj. 95% CI",
    "Adj. p-value")

# Word Doc output
ft <- flextable(regressionDF) %>% 
  colformat_double(big.mark=",", digits = 1, na_str = "N/A") %>%
  add_header_row(values = c("", "Baseline Analysis", "Adjusted Analysis"), 
                 top = T, colwidths = c(1, 3, 3)) %>% 
  width(width = 1.1) %>%
  width(j = 1, width = 2.5) %>%
  theme_vanilla() %>% 
  vline(j = c(1, 4), border = fp_border_default(), part = "all") %>% 
  align(i =1, align = "center", part = "header") 

ft

# LINEAR REGRESSIONS -------------------------------------------------------------------------------

lin_reg_vars <- data.frame(
  
  var_name = c(
    "sbp_mean_exit",
    "dbp_mean_exit", 
    "bmi", 
    "hemoglobin_a1c_result",
    "lipid_result"),

  var_label = c(
    "Systolic blood pressure (mmHg)",
    "Diastolic blood pressure (mmHg)",
    "BMI (kg/m^2)",
    "Hemoglobin A1c (%)",
    "Total cholesterol (mg/dL)") 
)
  

regressionDF <- data.frame(
        variable = character(),
        rd = numeric(),
        rd_ci = character(),
        rd_p = numeric(),
        adj.rd = character(),
        adj.rd_ci = character(), 
        adj.rd_p = character() 
)
 
 
for (v in unique(lin_reg_vars$var_name)) {
  
   # Adjusted for site only
  lm <- geeglm(get(v) ~ site + exit_viral_load_suppressed, 
              family = gaussian, data = vs_subset,
              id = hhid, corstr = "independence") 
  rd <- coef(lm)[["exit_viral_load_suppressedTRUE"]] # Mean Difference
  lm.se <- summary(lm)$coef["exit_viral_load_suppressedTRUE",2] # SE
  rd_ci <- c(coef(lm)[["exit_viral_load_suppressedTRUE"]] - qnorm(0.975)*lm.se, 
                coef(lm)[["exit_viral_load_suppressedTRUE"]] + qnorm(0.975)*lm.se) # 95% CI
  rd_p <- summary(lm)$coef["exit_viral_load_suppressedTRUE",4]

  # Adjusted for site, age, gender, smoking 
  
  adj.lm <- geeglm(get(v) ~  site + age_cat + genderR + smokingR + exit_viral_load_suppressed, 
              family = gaussian, data = vs_subset,
              id = hhid, corstr = "independence") 
  adj.rd <- coef(adj.lm)[["exit_viral_load_suppressedTRUE"]] # Mean Difference
  adj.lm.se <- summary(adj.lm)$coef["exit_viral_load_suppressedTRUE",2] # SE
  adj.rd_ci <- c(coef(adj.lm)[["exit_viral_load_suppressedTRUE"]] - qnorm(0.975)*adj.lm.se, 
                  coef(adj.lm)[["exit_viral_load_suppressedTRUE"]] + qnorm(0.975)*adj.lm.se) # 95% CI
  adj.rd_p <- summary(adj.lm)$coef["exit_viral_load_suppressedTRUE",4]
  
  temp_row <- c(lin_reg_vars[lin_reg_vars$var_name == v, "var_label"], 
                as.numeric(round(rd, round_digits)), 
                paste0("(",
                       as.numeric(round(rd_ci, round_digits))[1], 
                       ",",
                       as.numeric(round(rd_ci, round_digits))[2],
                       ")"),
                as.numeric(round(rd_p, p_digits)),
                as.numeric(round(adj.rd, round_digits)), 
                paste0("(",
                       as.numeric(round(adj.rd_ci, round_digits))[1], 
                       ",",
                       as.numeric(round(adj.rd_ci, round_digits))[2],
                       ")"),
                as.numeric(round(adj.rd_p, p_digits)))
  
  regressionDF <- rbind(regressionDF, temp_row)

}
  
names(regressionDF) =
  c("Variable",
    "Mean Difference",
    "95% CI",
    "p-value",
    "Adj. Mean Difference",
    "Adj. 95% CI",
    "Adj. p-value")


# Word Doc output
ft <- flextable(regressionDF) %>% 
  colformat_double(big.mark=",", digits = 1, na_str = "N/A") %>%
  add_header_row(values = c("", "Baseline Analysis", "Adjusted Analysis"), 
                 top = T, colwidths = c(1, 3, 3)) %>% 
  width(width = 1.1) %>%
  width(j = 1, width = 2.5) %>%
  theme_vanilla()  %>% 
  vline(j = c(1, 4), border = fp_border_default(), part = "all") %>% 
  align(i =1, align = "center", part = "header") 

ft
```


## Appendix S3, Table 2: Cardiovascular risk among people virally suppressed versus those not virally suppressed at endline, in the community-based follow-up arm (N = 642).

```{r, echo = F, warning = F, message = F, ft.split = T, ft.keepnext = F, results = 'asis'}

# Subset to South Africa only and clinic arm only!

ncd_merged_subset <- readRDS(paste0(in_dir, "ncd_merged_subset.rds")) %>% 
  filter(country == "South Africa") %>% 
  mutate(site = factor (site,
                       levels = c("HSRC",
                                  "AHRI"))) %>% 
  mutate(armR = case_when(arm == "Clinic arm" ~ "Clinic follow-up",
                          arm == "Community arm" ~ "Community follow-up",
                          arm == "Hybrid arm" ~ "Community follow-up" )) %>% 
  filter(armR == "Community follow-up")
  
  
round_digits = 2
p_digits = 3

# DROP NA for GEE to run

vs_subset <- ncd_merged_subset %>% 
  filter(!is.na(exit_viral_load_result))

# POISSON REGRESSIONS --------------------------------------------------------------------------

reg_vars <- data.frame(
  
  var_name = c(
    "bp_hi_exit", 
    "overwt_exit", 
    "a1c_hi_exit",
    "smokingR"
   ),

  var_label = c(
    "Elevated BP",
    "Overweight (BMI >= 25)",
    "Elevated blood sugar (a1c >= 5.7)",
    "Current smoker [baseline]"
  ))
  
regressionDF <- data.frame(
        variable = character(),
        rr = numeric(),
        rr_ci = character(),
        rr_p = numeric(),
        adj.rr = character(),
        adj.rr_ci = character(), 
        adj.rr_p = character() 
    )

 
for (v in unique(reg_vars$var_name)) {

  # Adjusted for site only
  m <- geeglm(get(v) ~ site + exit_viral_load_suppressed, 
              family = poisson, data = vs_subset,
              id = hhid, corstr = "independence") 
  m.rr <- exp(coef(m)[["exit_viral_load_suppressedTRUE"]]) # Relative Risk
  m.se <- summary(m)$coef["exit_viral_load_suppressedTRUE",2] # SE
  m.rr_ci <- exp(c(coef(m)[["exit_viral_load_suppressedTRUE"]] - qnorm(0.975)*m.se, 
                  coef(m)[["exit_viral_load_suppressedTRUE"]] + qnorm(0.975)*m.se)) # RR: 95% CI 
  m.p <- summary(m)$coef["exit_viral_load_suppressedTRUE",4]
  
  # Adjusted for site, age, gender, smoking 
  
  if (v != "smokingR") {
  
  adj.m <- geeglm(get(v) ~ site + age_cat + genderR + smokingR + exit_viral_load_suppressed, 
              family = poisson, data = vs_subset,
              id = hhid, corstr = "independence") 
  
  adj.rr <- exp(coef(adj.m)[["exit_viral_load_suppressedTRUE"]]) # Relative Risk
  adj.se <- summary(adj.m)$coef["exit_viral_load_suppressedTRUE",2] # SE
  adj.rr_ci <- exp(c(coef(adj.m)[["exit_viral_load_suppressedTRUE"]] - qnorm(0.975)*adj.se, 
                  coef(adj.m)[["exit_viral_load_suppressedTRUE"]] + qnorm(0.975)*adj.se)) # RR: 95% CI with robust SE
  adj.p <- summary(adj.m)$coef["exit_viral_load_suppressedTRUE",4]
  
  }
  
  if (v == "smokingR") {
  
  adj.m <- geeglm(get(v) ~ site + age_cat + genderR + exit_viral_load_suppressed, 
              family = poisson, data = vs_subset,
              id = hhid, corstr = "independence") 
  
  adj.rr <- exp(coef(adj.m)[["exit_viral_load_suppressedTRUE"]]) # Relative Risk
  adj.se <- summary(adj.m)$coef["exit_viral_load_suppressedTRUE",2] # SE
  adj.rr_ci <- exp(c(coef(adj.m)[["exit_viral_load_suppressedTRUE"]] - qnorm(0.975)*adj.se, 
                  coef(adj.m)[["exit_viral_load_suppressedTRUE"]] + qnorm(0.975)*adj.se)) # RR: 95% CI with robust SE
  adj.p <- summary(adj.m)$coef["exit_viral_load_suppressedTRUE",4]
  
  }
  
  temp_row <- c(reg_vars[reg_vars$var_name == v, "var_label"], 
                as.numeric(round(m.rr, round_digits)), 
                paste0("(",
                       as.numeric(round(m.rr_ci, round_digits))[1], 
                       ",",
                       as.numeric(round(m.rr_ci, round_digits))[2],
                       ")"),
                as.numeric(round(m.p, p_digits)),
                as.numeric(round(adj.rr, round_digits)), 
                paste0("(",
                       as.numeric(round(adj.rr_ci, round_digits))[1], 
                       ",",
                       as.numeric(round(adj.rr_ci, round_digits))[2],
                       ")"),
                as.numeric(round(adj.p, p_digits)))
  
  regressionDF <- rbind(regressionDF, temp_row)
  
}
  
names(regressionDF) =
  c("Variable",
    "Relative Risk",
    "95% CI",
    "p-value",
    "Adj. Relative Risk",
    "Adj. 95% CI",
    "Adj. p-value")

# Word Doc output
ft <- flextable(regressionDF) %>% 
  colformat_double(big.mark=",", digits = 1, na_str = "N/A") %>%
  add_header_row(values = c("", "Baseline Analysis", "Adjusted Analysis"), 
                 top = T, colwidths = c(1, 3, 3)) %>% 
  width(width = 1.1) %>%
  width(j = 1, width = 2.5) %>%
  theme_vanilla() %>% 
  vline(j = c(1, 4), border = fp_border_default(), part = "all") %>% 
  align(i =1, align = "center", part = "header") 

ft

# LINEAR REGRESSIONS -------------------------------------------------------------------------------

lin_reg_vars <- data.frame(
  
  var_name = c(
    "sbp_mean_exit",
    "dbp_mean_exit", 
    "bmi", 
    "hemoglobin_a1c_result",
    "lipid_result"),

  var_label = c(
    "Systolic blood pressure (mmHg)",
    "Diastolic blood pressure (mmHg)",
    "BMI (kg/m^2)",
    "Hemoglobin A1c (%)",
    "Total cholesterol (mg/dL)") 
)
  

regressionDF <- data.frame(
        variable = character(),
        rd = numeric(),
        rd_ci = character(),
        rd_p = numeric(),
        adj.rd = character(),
        adj.rd_ci = character(), 
        adj.rd_p = character() 
)
 
 
for (v in unique(lin_reg_vars$var_name)) {
  
   # Adjusted for site only
  lm <- geeglm(get(v) ~ site + exit_viral_load_suppressed, 
              family = gaussian, data = vs_subset,
              id = hhid, corstr = "independence") 
  rd <- coef(lm)[["exit_viral_load_suppressedTRUE"]] # Mean Difference
  lm.se <- summary(lm)$coef["exit_viral_load_suppressedTRUE",2] # SE
  rd_ci <- c(coef(lm)[["exit_viral_load_suppressedTRUE"]] - qnorm(0.975)*lm.se, 
                coef(lm)[["exit_viral_load_suppressedTRUE"]] + qnorm(0.975)*lm.se) # 95% CI
  rd_p <- summary(lm)$coef["exit_viral_load_suppressedTRUE",4]

  # Adjusted for site, age, gender, smoking 
  
  adj.lm <- geeglm(get(v) ~  site + age_cat + genderR + smokingR + exit_viral_load_suppressed, 
              family = gaussian, data = vs_subset,
              id = hhid, corstr = "independence") 
  adj.rd <- coef(adj.lm)[["exit_viral_load_suppressedTRUE"]] # Mean Difference
  adj.lm.se <- summary(adj.lm)$coef["exit_viral_load_suppressedTRUE",2] # SE
  adj.rd_ci <- c(coef(adj.lm)[["exit_viral_load_suppressedTRUE"]] - qnorm(0.975)*adj.lm.se, 
                  coef(adj.lm)[["exit_viral_load_suppressedTRUE"]] + qnorm(0.975)*adj.lm.se) # 95% CI
  adj.rd_p <- summary(adj.lm)$coef["exit_viral_load_suppressedTRUE",4]
  
  temp_row <- c(lin_reg_vars[lin_reg_vars$var_name == v, "var_label"], 
                as.numeric(round(rd, round_digits)), 
                paste0("(",
                       as.numeric(round(rd_ci, round_digits))[1], 
                       ",",
                       as.numeric(round(rd_ci, round_digits))[2],
                       ")"),
                as.numeric(round(rd_p, p_digits)),
                as.numeric(round(adj.rd, round_digits)), 
                paste0("(",
                       as.numeric(round(adj.rd_ci, round_digits))[1], 
                       ",",
                       as.numeric(round(adj.rd_ci, round_digits))[2],
                       ")"),
                as.numeric(round(adj.rd_p, p_digits)))
  
  regressionDF <- rbind(regressionDF, temp_row)

}
  
names(regressionDF) =
  c("Variable",
    "Mean Difference",
    "95% CI",
    "p-value",
    "Adj. Mean Difference",
    "Adj. 95% CI",
    "Adj. p-value")


# Word Doc output
ft <- flextable(regressionDF) %>% 
  colformat_double(big.mark=",", digits = 1, na_str = "N/A") %>%
  add_header_row(values = c("", "Baseline Analysis", "Adjusted Analysis"), 
                 top = T, colwidths = c(1, 3, 3)) %>% 
  width(width = 1.1) %>%
  width(j = 1, width = 2.5) %>%
  theme_vanilla()  %>% 
  vline(j = c(1, 4), border = fp_border_default(), part = "all") %>% 
  align(i =1, align = "center", part = "header") 

ft
```


### Page Break

## Appendix S3, Table 3: Coefficients for interaction term for cardiovascular risk for persons virally suppressed versus not suppressed at endline in South Africa (N = 983).

```{r, echo = F, warning = F, message = F, ft.split = T, ft.keepnext = F, results = 'asis'}

# DROP NA for GEE to run

ncd_merged_subset <- readRDS(paste0(in_dir, "ncd_merged_subset.rds")) %>% 
  filter(country == "South Africa") %>% 
  mutate(site = factor (site,
                       levels = c("HSRC",
                                  "AHRI"))) %>% 
  mutate(armR = case_when(arm == "Clinic arm" ~ "Clinic follow-up",
                          arm == "Community arm" ~ "Community follow-up",
                          arm == "Hybrid arm" ~ "Community follow-up" )) 

vs_subset <- ncd_merged_subset %>% 
  filter(!is.na(exit_viral_load_result))

# POISSON REGRESSIONS --------------------------------------------------------------------------

reg_vars <- data.frame(
  
  var_name = c(
    "bp_hi_exit", 
    "overwt_exit", 
    "a1c_hi_exit",
   # "total_cholesterol_hi_exit",
    "smokingR"
   ),

  var_label = c(
    "Elevated BP",
    "Overweight (BMI >= 25)",
    "Elevated blood sugar (a1c >= 5.7)",
   # "Elevated lipids (total cholesterol >= 200)",
    "Current smoker [baseline]"
  ))
  
regressionDF <- data.frame(
        variable = character(),
        rr = numeric(),
        rr_ci = character(),
        rr_p = numeric(),
        adj.rr = character(),
        adj.rr_ci = character(), 
        adj.rr_p = character() 
    )
 
for (v in unique(reg_vars$var_name)) {

  # Adjusted for site only
  m <- geeglm(get(v) ~ site + exit_viral_load_suppressed*armR, 
              family = poisson, data = vs_subset,
              id = hhid, corstr = "independence") 
  m.rr <- exp(coef(m)[["exit_viral_load_suppressedTRUE:armRCommunity follow-up"]]) # Relative Risk
  m.se <- summary(m)$coef["exit_viral_load_suppressedTRUE:armRCommunity follow-up",2] # SE
  m.rr_ci <- exp(c(coef(m)[["exit_viral_load_suppressedTRUE:armRCommunity follow-up"]] - qnorm(0.975)*m.se, 
                  coef(m)[["exit_viral_load_suppressedTRUE:armRCommunity follow-up"]] + qnorm(0.975)*m.se)) # RR: 95% CI 
  m.p <- summary(m)$coef["exit_viral_load_suppressedTRUE:armRCommunity follow-up",4]
  
  # Adjusted for site, age, gender, smoking 
  
  if (v != "smokingR") {
  
  adj.m <- geeglm(get(v) ~ site + age_cat + genderR + smokingR + exit_viral_load_suppressed*armR, 
              family = poisson, data = vs_subset,
              id = hhid, corstr = "independence") 
  
  adj.rr <- exp(coef(adj.m)[["exit_viral_load_suppressedTRUE:armRCommunity follow-up"]]) # Relative Risk
  adj.se <- summary(adj.m)$coef["exit_viral_load_suppressedTRUE:armRCommunity follow-up",2] # SE
  adj.rr_ci <- exp(c(coef(adj.m)[["exit_viral_load_suppressedTRUE:armRCommunity follow-up"]] - qnorm(0.975)*adj.se, 
                  coef(adj.m)[["exit_viral_load_suppressedTRUE:armRCommunity follow-up"]] + qnorm(0.975)*adj.se)) # RR: 95% CI with robust SE
  adj.p <- summary(adj.m)$coef["exit_viral_load_suppressedTRUE:armRCommunity follow-up",4]
  
  }
  
  if (v == "smokingR") {
  
  adj.m <- geeglm(get(v) ~ site + age_cat + genderR + exit_viral_load_suppressed*armR, 
              family = poisson, data = vs_subset,
              id = hhid, corstr = "independence") 
  
  adj.rr <- exp(coef(adj.m)[["exit_viral_load_suppressedTRUE:armRCommunity follow-up"]]) # Relative Risk
  adj.se <- summary(adj.m)$coef["exit_viral_load_suppressedTRUE:armRCommunity follow-up",2] # SE
  adj.rr_ci <- exp(c(coef(adj.m)[["exit_viral_load_suppressedTRUE:armRCommunity follow-up"]] - qnorm(0.975)*adj.se, 
                  coef(adj.m)[["exit_viral_load_suppressedTRUE:armRCommunity follow-up"]] + qnorm(0.975)*adj.se)) # RR: 95% CI with robust SE
  adj.p <- summary(adj.m)$coef["exit_viral_load_suppressedTRUE:armRCommunity follow-up",4]
  
  }
  
  temp_row <- c(reg_vars[reg_vars$var_name == v, "var_label"], 
                as.numeric(round(m.rr, round_digits)), 
                paste0("(",
                       as.numeric(round(m.rr_ci, round_digits))[1], 
                       ",",
                       as.numeric(round(m.rr_ci, round_digits))[2],
                       ")"),
                as.numeric(round(m.p, p_digits)),
                as.numeric(round(adj.rr, round_digits)), 
                paste0("(",
                       as.numeric(round(adj.rr_ci, round_digits))[1], 
                       ",",
                       as.numeric(round(adj.rr_ci, round_digits))[2],
                       ")"),
                as.numeric(round(adj.p, p_digits)))
  
  regressionDF <- rbind(regressionDF, temp_row)
  
}
  
names(regressionDF) =
  c("Variable",
    "Relative Risk",
    "95% CI",
    "p-value",
    "Adj. Relative Risk",
    "Adj. 95% CI",
    "Adj. p-value")


# Word Doc output
ft <- flextable(regressionDF) %>% 
  colformat_double(big.mark=",", digits = 1, na_str = "N/A") %>%
  add_header_row(values = c("", "Baseline Analysis", "Adjusted Analysis"), 
                 top = T, colwidths = c(1, 3, 3)) %>% 
  width(width = 1.1) %>%
  width(j = 1, width = 2.5) %>%
  theme_vanilla() %>% 
  vline(j = c(1, 4), border = fp_border_default(), part = "all") %>% 
  align(i =1, align = "center", part = "header") 

ft

# LINEAR REGRESSIONS -------------------------------------------------------------------------------

lin_reg_vars <- data.frame(
  
  var_name = c(
    "sbp_mean_exit",
    "dbp_mean_exit", 
    "bmi", 
    "hemoglobin_a1c_result",
    "lipid_result"),

  var_label = c(
    "Systolic blood pressure (mmHg)",
    "Diastolic blood pressure (mmHg)",
    "BMI (kg/m^2)",
    "Hemoglobin A1c (%)",
    "Total cholesterol (mg/dL)") 
)
  

regressionDF <- data.frame(
        variable = character(),
        rd = numeric(),
        rd_ci = character(),
        rd_p = numeric(),
        adj.rd = character(),
        adj.rd_ci = character(), 
        adj.rd_p = character() 
    )
 
for (v in unique(lin_reg_vars$var_name)) {
  
   # Adjusted for site only
  lm <- geeglm(get(v) ~ site + exit_viral_load_suppressed*armR, 
              family = gaussian, data = vs_subset,
              id = hhid, corstr = "independence") 
  rd <- coef(lm)[["exit_viral_load_suppressedTRUE:armRCommunity follow-up"]] # Mean Difference
  lm.se <- summary(lm)$coef["exit_viral_load_suppressedTRUE:armRCommunity follow-up",2] # SE
  rd_ci <- c(coef(lm)[["exit_viral_load_suppressedTRUE:armRCommunity follow-up"]] - qnorm(0.975)*lm.se, 
                coef(lm)[["exit_viral_load_suppressedTRUE:armRCommunity follow-up"]] + qnorm(0.975)*lm.se) # 95% CI
  rd_p <- summary(lm)$coef["exit_viral_load_suppressedTRUE:armRCommunity follow-up",4]

  # Adjusted for site, age, gender, smoking 
  
  adj.lm <- geeglm(get(v) ~  site + age_cat + genderR + smokingR + exit_viral_load_suppressed*armR, 
              family = gaussian, data = vs_subset,
              id = hhid, corstr = "independence") 
  adj.rd <- coef(adj.lm)[["exit_viral_load_suppressedTRUE:armRCommunity follow-up"]] # Mean Difference
  adj.lm.se <- summary(adj.lm)$coef["exit_viral_load_suppressedTRUE:armRCommunity follow-up",2] # SE
  adj.rd_ci <- c(coef(adj.lm)[["exit_viral_load_suppressedTRUE:armRCommunity follow-up"]] - qnorm(0.975)*adj.lm.se, 
                  coef(adj.lm)[["exit_viral_load_suppressedTRUE:armRCommunity follow-up"]] + qnorm(0.975)*adj.lm.se) # 95% CI
  adj.rd_p <- summary(adj.lm)$coef["exit_viral_load_suppressedTRUE:armRCommunity follow-up",4]
  
  temp_row <- c(lin_reg_vars[lin_reg_vars$var_name == v, "var_label"], 
                as.numeric(round(rd, round_digits)), 
                paste0("(",
                       as.numeric(round(rd_ci, round_digits))[1], 
                       ",",
                       as.numeric(round(rd_ci, round_digits))[2],
                       ")"),
                as.numeric(round(rd_p, p_digits)),
                as.numeric(round(adj.rd, round_digits)), 
                paste0("(",
                       as.numeric(round(adj.rd_ci, round_digits))[1], 
                       ",",
                       as.numeric(round(adj.rd_ci, round_digits))[2],
                       ")"),
                as.numeric(round(adj.rd_p, p_digits)))
  
  regressionDF <- rbind(regressionDF, temp_row)
  
}
  
names(regressionDF) =
  c("Variable",
    "Mean Difference",
    "95% CI",
    "p-value",
    "Adj. Mean Difference",
    "Adj. 95% CI",
    "Adj. p-value")


# Word Doc output
ft <- flextable(regressionDF) %>% 
  colformat_double(big.mark=",", digits = 1, na_str = "N/A") %>%
  add_header_row(values = c("", "Baseline Analysis", "Adjusted Analysis"), 
                 top = T, colwidths = c(1, 3, 3)) %>% 
  width(width = 1.1) %>%
  width(j = 1, width = 2.5) %>%
  theme_vanilla()  %>% 
  vline(j = c(1, 4), border = fp_border_default(), part = "all") %>% 
  align(i =1, align = "center", part = "header") 

ft
```

** Note, we drop 27 participants without endline viral load available.

** This is the coefficient for VS * arm

## S4: Additional Figures


## S4 Figure 1: Distribution of clinical CVD measures, by arm [dashed lines are group medians]

```{r, echo = F, fig.height = 3.4, fig.width = 10, warning = F, message = F, results = 'hide'}
# Graph, by arm

df <- ncd_merged_subset %>% 
  mutate(`Trial arm` = armR)

alpha_level = 0.35

lp = "bottom" # legend position, for all distribution figures

# SBP        

cvd_cutoff1 = 120
cvd_cutoff2 = NA
cvd_label = "Systolic BP (mmHg)"

mu <- plyr::ddply(df, "`Trial arm`", summarise, grp.median=median(sbp_mean_exit, na.rm = T))
                
p1 <-  ggplot(data = df, aes(x = sbp_mean_exit, fill = `Trial arm`)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values=c("#1b9e77", "#d95f02")) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=`Trial arm`),
                 linetype="dashed") +
      scale_color_manual(values=c("#1b9e77", "#d95f02")) +
      theme_bw() +
      theme(legend.position = lp)
    
# DBP

cvd_cutoff1 = 80
cvd_cutoff2 = NA
cvd_label = "Diastolic BP (mmHg)"

mu <- plyr::ddply(df, "`Trial arm`", summarise, grp.median=median(dbp_mean_exit, na.rm = T))
                
p2 <-  ggplot(data = df, aes(x = dbp_mean_exit, fill = `Trial arm`)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values=c("#1b9e77", "#d95f02")) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=`Trial arm`),
                 linetype="dashed") +
      scale_color_manual(values=c("#1b9e77", "#d95f02")) +
      theme_bw() +
      theme(legend.position = lp)

# BMI

cvd_cutoff1 = 25
cvd_cutoff2 = 30
cvd_label = "BMI (kg/m^2)"

mu <- plyr::ddply(df, "`Trial arm`", summarise, grp.median=median(bmi, na.rm = T))
                
p3 <-  ggplot(data = df, aes(x = bmi, fill = `Trial arm`)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values=c("#1b9e77", "#d95f02")) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=`Trial arm`),
                 linetype="dashed") +
      scale_color_manual(values=c("#1b9e77", "#d95f02")) +
      theme_bw() +
      theme(legend.position = lp)

# A1c

cvd_cutoff1 = 5.7
cvd_cutoff2 = 6.5
cvd_label = "Hemoglobin A1c (%)"

mu <- plyr::ddply(df, "`Trial arm`", summarise, grp.median=median(hemoglobin_a1c_result, na.rm = T))
                
p4 <-  ggplot(data = df, aes(x = hemoglobin_a1c_result, fill = `Trial arm`)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values=c("#1b9e77", "#d95f02")) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=`Trial arm`),
                 linetype="dashed") +
      scale_color_manual(values=c("#1b9e77", "#d95f02")) +
      theme_bw() +
      theme(legend.position = lp)

# Cholesterol


cvd_cutoff1 = 200
cvd_cutoff2 = 240
cvd_label = "Total cholesterol (mg/dL"

mu <- plyr::ddply(df, "`Trial arm`", summarise, grp.median=median(lipid_result, na.rm = T))
                
p5 <-  ggplot(data = df, aes(x = lipid_result, fill = `Trial arm`)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values=c("#1b9e77", "#d95f02")) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color= `Trial arm`),
                 linetype="dashed") +
      scale_color_manual(values=c("#1b9e77", "#d95f02")) +
      theme_bw() +
      theme(legend.position = lp)

# Arrange!

ggarrange(p1, p3, p4, p5, # skip DBP
          ncol = 2)

```


### Page Break

## S4 Figure 2: Distribution of cardiovascular risk, by viral suppression status at exit [dashed lines are group medians]

```{r, echo = F, fig.height = 3.4, fig.width = 10, warning = F, message = F, results = 'hide'}
df = ncd_merged_subset %>%  filter(exit_viral_load_suppressedR != "Missing")
alpha_level = 0.5
lp = "bottom" # legend position, for all distribution figures

# Excluding missing

vs_colors = c("#00A08A", "#FF0000")
vs_title = "Virally suppressed at exit"

# SBP        

cvd_cutoff1 = 120
cvd_cutoff2 = NA
cvd_label = "Systolic BP (mmHg)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(sbp_mean_exit, na.rm = T))
                
p1 <-  ggplot(df, aes(x = sbp_mean_exit, fill = exit_viral_load_suppressedR)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values = vs_colors) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values= vs_colors) +
      guides(fill=guide_legend(title = vs_title)) +
      guides(color=guide_legend(title = vs_title)) +
      theme_bw() +
      theme(legend.position = lp)
    
# DBP

cvd_cutoff1 = 80
cvd_cutoff2 = NA
cvd_label = "Diastolic BP (mmHg)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(dbp_mean_exit, na.rm = T))
                
p2 <-  ggplot(df, aes(x = dbp_mean_exit, fill = exit_viral_load_suppressedR)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values= vs_colors) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values= vs_colors) +
      guides(fill=guide_legend(title=vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw() +
      theme(legend.position = lp)

# BMI

cvd_cutoff1 = 25
cvd_cutoff2 = 30
cvd_label = "BMI (kg/m^2)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(bmi, na.rm = T))
                
p3 <-  ggplot(df, aes(x = bmi, fill = exit_viral_load_suppressedR)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values = vs_colors) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values = vs_colors) +
      guides(fill=guide_legend(title=vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw() +
      theme(legend.position = lp)

# A1c

cvd_cutoff1 = 5.7
cvd_cutoff2 = 6.5
cvd_label = "Hemoglobin A1c (%)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(hemoglobin_a1c_result, na.rm = T))
                
p4 <-  ggplot(df, aes(x = hemoglobin_a1c_result, fill = exit_viral_load_suppressedR)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values = vs_colors) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values = vs_colors) +
      guides(fill=guide_legend(title=vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw() +
      theme(legend.position = lp)

# Cholesterol


cvd_cutoff1 = 200
cvd_cutoff2 = 240
cvd_label = "Total cholesterol (mg/dL)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(lipid_result, na.rm = T))
                
p5 <-  ggplot(df, aes(x = lipid_result, fill = exit_viral_load_suppressedR)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values = vs_colors) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values = vs_colors) +
      guides(fill=guide_legend(title=vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw() +
      theme(legend.position = lp)

# Arrange!

ggarrange(p1, p3, p4, p5, # skip DBP
          ncol = 2)


```


### Page Break

## S4 Figure 3: Distribution, by VS status at endline [dashed lines are group medians] - CLINIC ONLY

```{r, echo = F, fig.height = 3.4, fig.width = 10, warning = F, message = F, results = 'hide'}
df = ncd_merged_subset %>%  
  filter(exit_viral_load_suppressedR != "Missing") %>% 
  filter(armR == "Clinic follow-up")

alpha_level = 0.5

# Excluding missing

vs_colors = c("#00A08A", "#FF0000")
vs_title = "Virally suppressed at exit"

# SBP        

cvd_cutoff1 = 120
cvd_cutoff2 = NA
cvd_label = "Systolic BP (mmHg)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(sbp_mean_exit, na.rm = T))
                
p1 <-  ggplot(df, aes(x = sbp_mean_exit, fill = exit_viral_load_suppressedR)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values = vs_colors) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values= vs_colors) +
      guides(fill=guide_legend(title= vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw()  +
      theme(legend.position = lp)
    
# DBP

cvd_cutoff1 = 80
cvd_cutoff2 = NA
cvd_label = "Diastolic BP (mmHg)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(dbp_mean_exit, na.rm = T))
                
p2 <-  ggplot(df, aes(x = dbp_mean_exit, fill = exit_viral_load_suppressedR)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values= vs_colors) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values= vs_colors) +
      guides(fill=guide_legend(title=vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw()  +
      theme(legend.position = lp)

# BMI

cvd_cutoff1 = 25
cvd_cutoff2 = 30
cvd_label = "BMI (kg/m^2)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(bmi, na.rm = T))
                
p3 <-  ggplot(df, aes(x = bmi, fill = exit_viral_load_suppressedR)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values = vs_colors) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values = vs_colors) +
      guides(fill=guide_legend(title=vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw()  +
      theme(legend.position = lp)

# A1c

cvd_cutoff1 = 5.7
cvd_cutoff2 = 6.5
cvd_label = "Hemoglobin A1c (%)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(hemoglobin_a1c_result, na.rm = T))
                
p4 <-  ggplot(df, aes(x = hemoglobin_a1c_result, fill = exit_viral_load_suppressedR)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values = vs_colors) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values = vs_colors) +
      guides(fill=guide_legend(title=vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw()  +
      theme(legend.position = lp)

# Cholesterol


cvd_cutoff1 = 200
cvd_cutoff2 = 240
cvd_label = "Total cholesterol (mg/dL)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(lipid_result, na.rm = T))
                
p5 <-  ggplot(df, aes(x = lipid_result, fill = exit_viral_load_suppressedR)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values = vs_colors) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values = vs_colors) +
      guides(fill=guide_legend(title=vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw()  +
      theme(legend.position = lp)

# Arrange!

ggarrange(p1, p3, p4, p5, # skip DBP
          ncol = 2)

```

### Page break

## S4 Figure 3: Distribution, by VS status at endline [dashed lines are group medians] - COMMUNITY ONLY

```{r, echo = F, fig.height = 3.4, fig.width = 10, warning = F, message = F, results = 'hide'}
df = ncd_merged_subset %>%  
  filter(exit_viral_load_suppressedR != "Missing") %>% 
  filter(armR == "Community follow-up")

alpha_level = 0.5

# Excluding missing

vs_colors = c("#00A08A", "#FF0000")
vs_title = "Virally suppressed at exit"

# SBP        

cvd_cutoff1 = 120
cvd_cutoff2 = NA
cvd_label = "Systolic BP (mmHg)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(sbp_mean_exit, na.rm = T))
                
p1 <-  ggplot(df, aes(x = sbp_mean_exit, fill = exit_viral_load_suppressedR)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values = vs_colors) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values= vs_colors) +
      guides(fill=guide_legend(title=vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw()  +
      theme(legend.position = lp)
    
# DBP

cvd_cutoff1 = 80
cvd_cutoff2 = NA
cvd_label = "Diastolic BP (mmHg)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(dbp_mean_exit, na.rm = T))
                
p2 <-  ggplot(df, aes(x = dbp_mean_exit, fill = exit_viral_load_suppressedR)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values= vs_colors) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values= vs_colors) +
      guides(fill=guide_legend(title=vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw()  +
      theme(legend.position = lp)

# BMI

cvd_cutoff1 = 25
cvd_cutoff2 = 30
cvd_label = "BMI (kg/m^2)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(bmi, na.rm = T))
                
p3 <-  ggplot(df, aes(x = bmi, fill = exit_viral_load_suppressedR)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values = vs_colors) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values = vs_colors) +
      guides(fill=guide_legend(title=vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw()  +
      theme(legend.position = lp)

# A1c

cvd_cutoff1 = 5.7
cvd_cutoff2 = 6.5
cvd_label = "Hemoglobin A1c (%)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(hemoglobin_a1c_result, na.rm = T))
                
p4 <-  ggplot(df, aes(x = hemoglobin_a1c_result, fill = exit_viral_load_suppressedR)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values = vs_colors) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values = vs_colors) +
      guides(fill=guide_legend(title=vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw()  +
      theme(legend.position = lp)

# Cholesterol


cvd_cutoff1 = 200
cvd_cutoff2 = 240
cvd_label = "Total cholesterol (mg/dL)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(lipid_result, na.rm = T))
                
p5 <-  ggplot(df, aes(x = lipid_result, fill = exit_viral_load_suppressedR)) + 
      geom_density(alpha = alpha_level) +   
      scale_fill_manual(values = vs_colors) +
      xlab(cvd_label) +
      geom_vline(xintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_vline(data=mu, aes(xintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values = vs_colors) +
      guides(fill=guide_legend(title=vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw()  +
      theme(legend.position = lp)

# Arrange!

ggarrange(p1, p3, p4, p5, # skip DBP
          ncol = 2)


```

### Page Break

## S4 Figure 5: Distribution of CVD variables by age

```{r, echo = F, fig.height = 3.4, fig.width = 10, warning = F, message = F, results = 'hide'}
df = ncd_merged_subset %>%
  filter(exit_viral_load_suppressedR != "Missing")

alpha_low = 0.7
alpha_hi = 0.8
point_size = 2
lp = "bottom" # legend position, for all distribution figures


# Excluding missing

vs_colors = c("#00A08A", "#FF0000")
vs_title = "Virally suppressed at exit"

# SBP        

cvd_cutoff1 = 120
cvd_cutoff2 = NA
cvd_label = "Systolic BP (mmHg)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(sbp_mean_exit, na.rm = T))
                
p1 <- ggplot(df, aes(x = age, y = sbp_mean_exit, group = exit_viral_load_suppressedR)) + 
      geom_point(aes(color = exit_viral_load_suppressedR),
                     alpha = alpha_hi, size = point_size) +   
      ylab(cvd_label) + xlab("Age") +
      geom_hline(yintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_hline(data=mu, aes(yintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values = vs_colors) +
      scale_fill_manual(values = vs_colors) +
      guides(fill=guide_legend(title=vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw() +
      theme(legend.position = lp)
    
# DBP

cvd_cutoff1 = 80
cvd_cutoff2 = NA
cvd_label = "Diastolic BP (mmHg)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(dbp_mean_exit, na.rm = T))
                
p2 <-  ggplot(df, aes(x = age, y = dbp_mean_exit, group = exit_viral_load_suppressedR)) + 
      geom_point(aes(color = exit_viral_load_suppressedR),
                     alpha = alpha_hi, size = point_size) +   
      ylab(cvd_label) + xlab("Age") +
      geom_hline(yintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_hline(data=mu, aes(yintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values = vs_colors) +
      scale_fill_manual(values = vs_colors) +
      guides(fill=guide_legend(title=vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw() +
      theme(legend.position = lp)

# BMI

cvd_cutoff1 = 25
cvd_cutoff2 = 30
cvd_label = "BMI (kg/m^2)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(bmi, na.rm = T))
                
p3 <-  ggplot(df, aes(x = age, y = bmi, group = exit_viral_load_suppressedR)) + 
      geom_point(aes(color = exit_viral_load_suppressedR),
                 alpha = alpha_hi, size = point_size) +     
      ylab(cvd_label) + xlab("Age") +
      geom_hline(yintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_hline(data=mu, aes(yintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values = vs_colors) +
      scale_fill_manual(values = vs_colors) +
      guides(fill=guide_legend(title=vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw() +
      theme(legend.position = lp)

# A1c

cvd_cutoff1 = 5.7
cvd_cutoff2 = 6.5
cvd_label = "Hemoglobin A1c (%)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(hemoglobin_a1c_result, na.rm = T))
                
p4 <-  ggplot(df, aes(x = age, y = hemoglobin_a1c_result, group = exit_viral_load_suppressedR)) + 
      geom_point(aes(color = exit_viral_load_suppressedR),
                 alpha = alpha_hi, size = point_size) +    
      ylab(cvd_label) + xlab("Age") +
      geom_hline(yintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_hline(data=mu, aes(yintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values = vs_colors) +
      scale_fill_manual(values = vs_colors) +
      guides(fill=guide_legend(title=vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw() +
      theme(legend.position = lp)

# Cholesterol


cvd_cutoff1 = 200
cvd_cutoff2 = 240
cvd_label = "Total cholesterol (mg/dL)"

mu <- plyr::ddply(df, "exit_viral_load_suppressedR", summarise, grp.median=median(lipid_result, na.rm = T))

p5 <-  ggplot(df, aes(x = age, y = lipid_result, group = exit_viral_load_suppressedR)) + 
      geom_point(aes(color = exit_viral_load_suppressedR),
                 alpha = alpha_hi, size = point_size) +       
      ylab(cvd_label) + xlab("Age") +
      geom_hline(yintercept = c(cvd_cutoff1, cvd_cutoff2), size = .6) +
      geom_hline(data=mu, aes(yintercept=grp.median, color=exit_viral_load_suppressedR),
                 linetype="dashed") +
      scale_color_manual(values = vs_colors) +
      scale_fill_manual(values = vs_colors) +
      guides(fill=guide_legend(title=vs_title)) +
      guides(color=guide_legend(title=vs_title)) +
      theme_bw() +
      theme(legend.position = lp)

# Arrange!

ggarrange(p1, p3, p4, p5, # skip DBP
          ncol = 2)

```
### Page Break

```{r, include = F, echo = F}
# NUMBER PLUGGING (rough)

ncd_merged_subset %>%  filter(armR == "Community follow-up") %>%filter(is.na(exit_viral_load_result)) %>%  nrow()

ncd_merged_subset %>%  filter(armR == "Clinic follow-up") %>%  filter(is.na(exit_viral_load_result)) %>%  nrow()
```
